---
title: "Baseline long survey"
author: "MERL Report"
date: "2025-06-02"
output: word_document
toc: true
---
\pagebreak
```{r include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,  
  message = FALSE,  
  warning = FALSE 
  
)
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
library(httr)
library(jsonlite)
library(tidyverse)
library(readxl)
library(tidyr)
library(dplyr)
library(here)
library(skimr)
library(janitor)
library(writexl)
library(ggplot2)
library(magick)
library(knitr)
```

## Accessing data

The data was exported from CommCare on 19/05/2025. A subset of the indicators was selected depending on the goal of the calculation and the indicators needed.

```{r echo=FALSE, message=FALSE, warning=FALSE}
Mangwana_Baseline_Survey <- read_excel("Mangwana - Baseline Survey.xlsx", 
                                       sheet = "Forms")

```

```{r echo=FALSE, message=FALSE, warning=FALSE}
Selected_Child_indicators <- Mangwana_Baseline_Survey %>% 
  select(formid, form.Section_II_group.voc_tem_um_filho_entre_0_e_24_meses,form.Section_II_group.alguma_vez_qual__o_nome_da_criana_entre_0_e_24_meses_foi_amamentado, form.Section_II_group.llquidos_formula_infantil,form.Section_II_group.em_quanto_tempo_depois_do_nascimento_qual__o_nome_da_criana_entre_0_e_24_me, form.Section_II_group.leite_de_origem_animal_incluindo_lquido_ou_em_p,form.Section_II_group.achocolatado_como_milo_cremora_ou_leite_condensado,
         form.Section_II_group.sumos_ou_sumos_em_p,`form.Section_II_group.refrescos_como_coca-cola_fanta_frozy_ou_fizz_ou_bebidas_energticas_como_o_r`, form.Section_II_group.ch_caf_ou_bebidas__base_de_plantas_ou_ervas, form.Section_II_group.sopa_ou_caldo, form.Section_II_group.iogurte, form.Section_II_group.arroz_po_massa_esparguete_xima_de_farinha_de_milho_processada_papas_de_fari,form.Section_II_group.brculos_espinafres_folhas_de_moringa_folhas_de_amaranto_ou_quiabo_de_folha,form.Section_II_group.camaro_voador_caracol_da_terra_trmita_ou_ishwa,
         form.Section_II_group.xima_ou_papas_de_milho_no_processado_mexoeira_mapira_maaroca_po_integral_ou,form.Section_II_group.batata_batata_doce_branca_inhame_mandioca_xima_de_mandioca_ou_papas_de_mand,form.Section_II_group.feijo_comum_feijo_nhemba_ervilha_feijo_boer_feijo_jugo_feijo_soroco_ou_soja, form.Section_II_group.cenoura_abbora_ou_batata_doce_de_polpa_alaranjada,form.Section_II_group.couve_folhas_de_abobora_folhas_de_cacana_folhas_de_batata_doce_folha_de_fei, 
         form.Section_II_group.tomate_repolho_quiabo_beringela_ou_cogumelos, form.Section_II_group.alface_pepino_feijo_verde_ou_pimento_verde, form.Section_II_group.manga_madura_papaia_madura_ou_maracuj, form.Section_II_group.laranja_ou_tangerinas,form.Section_II_group.bananas_melancia_abacate_lichia_caju_anans_ou_malambe, form.Section_II_group.ma_pra_goiaba_massala_ata_mapfilo_tintsiva_ou_mafurra, form.Section_II_group.bolos_bolinhos_bolachas_doces_argolas_fritas_bolas_de_berlim_ou_fiosso, 
         form.Section_II_group.ovos, form.Section_II_group.queijo, form.Section_II_group.paloni_salsichas_ou_enchidos_como_chourio_linguia_rachel_russian_ou_vorse, form.Section_II_group.carne_de_vaca_carne_de_cabrito_carne_de_ovelha_gazela_ou_bufalo, form.Section_II_group.carne_de_porco_carne_de_ratazana_ou_coelho, form.Section_II_group.galinha_pato_peru_codorniz_ou_passarinhos, form.Section_II_group.peixe_fresco_ou_seco_camaro_fresco_ou_seco_caranguejo_lulas_ou_ameijoa, 
         form.Section_II_group.amendoim_manteiga_de_amendoim_amendoim_modo_castanhas_de_caj_ou_sementes_de, form.Section_II_group.chips_pipocas_de_pacote_ou_niknaks, form.Section_II_group.massa_instantnea,form.Section_II_group.batatas_fritas_badjia_peixe_frito_ou_frango_frito,`form.Section_II_group.copy-1-of-leo_de_palma_vermelho`,form.Section_II_group.chupa_chupa_ou_doces_bombom_chocolate_sorvete_ou_gelinho,form.Section_II_group.leo_de_palma_vermelho) %>% 
  
  rename(have_child = form.Section_II_group.voc_tem_um_filho_entre_0_e_24_meses,
         breastfed = form.Section_II_group.alguma_vez_qual__o_nome_da_criana_entre_0_e_24_meses_foi_amamentado,
         early_breastfeed = form.Section_II_group.em_quanto_tempo_depois_do_nascimento_qual__o_nome_da_criana_entre_0_e_24_me,
         infant_formula = form.Section_II_group.llquidos_formula_infantil, 
         animal_milk = form.Section_II_group.leite_de_origem_animal_incluindo_lquido_ou_em_p,
         chocolate_milk = form.Section_II_group.achocolatado_como_milo_cremora_ou_leite_condensado,
         juices = form.Section_II_group.sumos_ou_sumos_em_p,
         soft_drinks = `form.Section_II_group.refrescos_como_coca-cola_fanta_frozy_ou_fizz_ou_bebidas_energticas_como_o_r`, 
         plant_base_drink = form.Section_II_group.ch_caf_ou_bebidas__base_de_plantas_ou_ervas, 
         soups_broth = form.Section_II_group.sopa_ou_caldo, 
         yoghurt = form.Section_II_group.iogurte, 
         processed_porridge = form.Section_II_group.arroz_po_massa_esparguete_xima_de_farinha_de_milho_processada_papas_de_fari,
         green_leafy_vegetables = form.Section_II_group.brculos_espinafres_folhas_de_moringa_folhas_de_amaranto_ou_quiabo_de_folha,#Broccoli, spinach, moringa leaves, amaranth leaves or okra leaves
         shrimp_snails = form.Section_II_group.camaro_voador_caracol_da_terra_trmita_ou_ishwa,# Flying shrimp, land snail, termite or ishwa
         unprocessed_porridge = form.Section_II_group.xima_ou_papas_de_milho_no_processado_mexoeira_mapira_maaroca_po_integral_ou, # Xima or unprocessed corn porridge, millet, mapira, corn cob, wholemeal bread or corn cob popcorn
         root_crop_porridge = form.Section_II_group.batata_batata_doce_branca_inhame_mandioca_xima_de_mandioca_ou_papas_de_mand,
         beans = form.Section_II_group.feijo_comum_feijo_nhemba_ervilha_feijo_boer_feijo_jugo_feijo_soroco_ou_soja, 
         orange_vegetables = form.Section_II_group.cenoura_abbora_ou_batata_doce_de_polpa_alaranjada,# Carrot, pumpkin or orange-fleshed sweet potato
         leafy_vegetables = form.Section_II_group.couve_folhas_de_abobora_folhas_de_cacana_folhas_de_batata_doce_folha_de_fei, # Cabbage, pumpkin leaves, cacana leaves, sweet potato leaves, cowpea leaves or cassava leaves
         tomato_cabbage_mushroom = form.Section_II_group.tomate_repolho_quiabo_beringela_ou_cogumelos, # Tomato, cabbage, okra, eggplant or mushrooms
         salad_vegetables = form.Section_II_group.alface_pepino_feijo_verde_ou_pimento_verde, # Lettuce, cucumber, green beans or green pepper
         yellow_fruits = form.Section_II_group.manga_madura_papaia_madura_ou_maracuj, # Ripe mango, ripe papaya or passion fruit
         citrus = form.Section_II_group.laranja_ou_tangerinas,
         long_cycle_fruits = form.Section_II_group.bananas_melancia_abacate_lichia_caju_anans_ou_malambe, # Bananas, watermelon, avocado, lychee, cashew, pineapple or malambe
         apples = form.Section_II_group.ma_pra_goiaba_massala_ata_mapfilo_tintsiva_ou_mafurra, # Apple, pear, guava, massala, ata, mapfilo, tintsiva, or mafurra
         cakes = form.Section_II_group.bolos_bolinhos_bolachas_doces_argolas_fritas_bolas_de_berlim_ou_fiosso, # Cakes, cupcakes, sweet biscuits, fried rings, Berlin balls or yarn
         eggs = form.Section_II_group.ovos, 
         cheese = form.Section_II_group.queijo, 
         sausages = form.Section_II_group.paloni_salsichas_ou_enchidos_como_chourio_linguia_rachel_russian_ou_vorse, # Paloni, sausages, or sausages like chorizo, linguiça, rachel, Russian or vorse
         meat = form.Section_II_group.carne_de_vaca_carne_de_cabrito_carne_de_ovelha_gazela_ou_bufalo, # Beef, goat meat, sheep meat, gazelle or buffalo
         pork_rabbit = form.Section_II_group.carne_de_porco_carne_de_ratazana_ou_coelho, # Pork, rat or rabbit meat
         poultry = form.Section_II_group.galinha_pato_peru_codorniz_ou_passarinhos, # Chicken, duck, turkey, quail or birds
         fish = form.Section_II_group.peixe_fresco_ou_seco_camaro_fresco_ou_seco_caranguejo_lulas_ou_ameijoa, # Fresh or dried fish, fresh or dried shrimp, crab, squid or clams
         nuts = form.Section_II_group.amendoim_manteiga_de_amendoim_amendoim_modo_castanhas_de_caj_ou_sementes_de, # Peanuts, peanut butter, ground peanuts, cashews or pumpkin seeds
         popcorns = form.Section_II_group.chips_pipocas_de_pacote_ou_niknaks, # Chips, popcorn or NikNaks
         instant_pasta = form.Section_II_group.massa_instantnea,
         fries = form.Section_II_group.batatas_fritas_badjia_peixe_frito_ou_frango_frito, # Deep fried foods
         palm_oil = form.Section_II_group.leo_de_palma_vermelho, 
         fast_foods = `form.Section_II_group.copy-1-of-leo_de_palma_vermelho`, # KFC, Debonairs Pizza, Teka Famba, Burger House, Flaming Dogs or other places that serve pizza or burgers
         sweets = form.Section_II_group.chupa_chupa_ou_doces_bombom_chocolate_sorvete_ou_gelinho)  %>% # Lollipops or sweets, bonbons, chocolate, ice cream or popsicles
   

  mutate(
    across(c(have_child,breastfed,infant_formula,animal_milk,chocolate_milk,juices,soft_drinks,plant_base_drink,soups_broth,yoghurt,processed_porridge,shrimp_snails,unprocessed_porridge,root_crop_porridge,
             beans, orange_vegetables,leafy_vegetables,green_leafy_vegetables,tomato_cabbage_mushroom,salad_vegetables,yellow_fruits,citrus,long_cycle_fruits,apples,cakes,eggs,cheese,sausages,meat,pork_rabbit,poultry,
             fish,nuts,popcorns,instant_pasta,fries,palm_oil,fast_foods,sweets), ~ ifelse(. == "sim", 1,0))
  ) %>% 
  filter(have_child == 1) %>%
  
  mutate(
    ## Dietary Diversity Score for the entire children population
    dds = (rowSums(tibble(processed_porridge, unprocessed_porridge, root_crop_porridge) == 1) > 0) + # Grains, roots, tubers
      (rowSums(tibble(beans) == 1) > 0) + # Pulses
      (rowSums(tibble(nuts) == 1) > 0) + # Nuts and seeds
      (rowSums(tibble(animal_milk, cheese, yoghurt) == 1) > 0) + # Dairy
      (rowSums(tibble(meat, sausages, pork_rabbit, poultry, fish, shrimp_snails) == 1) > 0) + # Meat, poultry, fish
      (rowSums(tibble(green_leafy_vegetables, leafy_vegetables) == 1) > 0) + # Dark green leafy vegetables
      (rowSums(tibble(eggs) == 1) > 0) + # Eggs
      (rowSums(tibble(orange_vegetables, tomato_cabbage_mushroom, yellow_fruits, citrus, apples) == 1) > 0) + # Vitamin A-rich fruits and vegetables
      (rowSums(tibble(long_cycle_fruits) == 1) > 0),# Other fruits
    all_5 = (rowSums(tibble(processed_porridge, unprocessed_porridge, root_crop_porridge) == 1) > 0) + # Starchy staples
      (rowSums(tibble(green_leafy_vegetables, leafy_vegetables, orange_vegetables, tomato_cabbage_mushroom, salad_vegetables) == 1) > 0) + # Vegetables
      (rowSums(tibble(yellow_fruits, citrus,long_cycle_fruits, apples) == 1) > 0) + # Fruits
      (rowSums(tibble(beans,nuts) == 1) > 0) + # Pulses, nuts and seeds
      (rowSums(tibble(animal_milk, yoghurt, eggs, cheese, sausages, meat, poultry, fish, shrimp_snails) == 1) > 0), # Animal-source foods
    ncd_protect = (rowSums(tibble(unprocessed_porridge) == 1) > 0) + # Whole grain
      (rowSums(tibble(beans) == 1) > 0) + # Pulses
      (rowSums(tibble(nuts) == 1) > 0) + # Nuts and seeds
      (rowSums(tibble(citrus) == 1) > 0) + # Citrus
      (rowSums(tibble(orange_vegetables) == 1) > 0) + # Vitamin A-rich orange vegetable
      (rowSums(tibble(green_leafy_vegetables, leafy_vegetables) == 1) > 0) + # Dark green leafy vegetables
      (rowSums(tibble(apples, yellow_fruits) == 1) > 0) + # Vitamin A-rich fruits
      (rowSums(tibble(tomato_cabbage_mushroom) == 1) > 0) + # Other vegetables
      (rowSums(tibble(long_cycle_fruits) == 1) > 0),# Other fruits
    ncd_risk = (rowSums(tibble(chocolate_milk, juices, soft_drinks) == 1) > 0) + # Represents: Soft drinks. I added juices because it was not clear from the survey whether natural fruit juice or otherwise.
      (rowSums(tibble(cakes) == 1) > 0) + # Baked/grain-based sweets
      (rowSums(tibble(sweets) == 1) > 0) + # Other sweets
      2 * (rowSums(tibble(sausages) == 1) > 0) + # Processed meat
      (rowSums(tibble(meat, pork_rabbit) == 1) > 0) + # Unprocessed meat
      (rowSums(tibble(fries) == 1) > 0) + # Deep fried food
      (rowSums(tibble(fast_foods, instant_pasta) == 1) > 0) + # Fast food & instant noodles
      (rowSums(tibble(popcorns) == 1) > 0), # Packaged ultra-processed salty snacks
    dds_binary = ifelse(dds >= 5, 1,0), # Calculating binary DDS
    
    all_5_binary = ifelse(all_5 == 5, 1,0), # Calculating binary All- 5
    
    ncd_protect_binary = ifelse(ncd_protect >= 5, 1,0), # Calculating binary NCD protect
    
    ncd_risk_binary = ifelse(ncd_risk >= 5, 1,0), # Calculating binary NCD protect
    
    gdr_score = (ncd_protect - ncd_risk) + 9, # Calculating General Dietary Recommendation (GDR score)
    
    ## Calculating various all 5 food groups for a graph
    starchy_staple = if_else(rowSums(across(c(processed_porridge, unprocessed_porridge, root_crop_porridge)) == 1) > 0, 1, 0),
    Vegetables = if_else(rowSums(across(c(green_leafy_vegetables, leafy_vegetables, orange_vegetables, 
                                          tomato_cabbage_mushroom, salad_vegetables)) == 1) > 0, 1, 0),
    fruits = if_else(rowSums(across(c(yellow_fruits, citrus, long_cycle_fruits, apples)) == 1) > 0, 1, 0),
    pulses = if_else(rowSums(across(c(beans,nuts)) == 1) > 0, 1, 0),
    protein = if_else(rowSums(across(c(animal_milk,yoghurt,eggs,cheese,sausages,meat,poultry,fish,shrimp_snails)) == 1) > 0, 1, 0)
  )

```

```{r}
mean_dds_score <- round(mean(Selected_Child_indicators$dds),1) # Calculating the average DDS score for the entire population
  
  mean_all_5_score <- round(mean(Selected_Child_indicators$all_5),1) # Calculating the average All 5 score for the entire population
  
  mean_ncd_protect_score <- round(mean(Selected_Child_indicators$ncd_protect),1) # Calculating the average NCD protect score for the entire population
  
  mean_ncd_risk_score <- round(mean(Selected_Child_indicators$ncd_risk),1) # Calculating the average NCD risk score for the entire population
  
  mean_gdr_score <- round(mean(Selected_Child_indicators$gdr_score),1) # Calculating the average GDR score for the entire population
  
   breastfeeding <- Selected_Child_indicators%>%
     filter(have_child == 1)
   
   breastfeeding  <- breastfeeding %>% 
     summarise(
       total = n(),
       breastfed = sum(breastfed == 1, na.rm = TRUE),
       percent_breastfed = (breastfed / total) * 100)
   
   immbreastfeeding <- Selected_Child_indicators%>%
     filter(breastfed == 1)
   
   immbreastfeeding  <- immbreastfeeding %>% 
     summarise(
       total = n(),
       imm_breastfed = sum(early_breastfeed == 1, na.rm = TRUE),
       percent_early_breastfed = (as.numeric(imm_breastfed) / total) * 100)
     
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
## Calculating the percentage of child dss scores above 5
#Calculating DDS and All-5 for children without breastfeeding

dds_percentage <- Selected_Child_indicators %>% 
  filter(have_child == 1, breastfed == 0) %>% 
  summarise(
    total_count = n(),
    count_five = sum(dds_binary == 1, na.rm = TRUE),
    percentage_five = (count_five/total_count) * 100,
  )

# print(dds_percentage, row.names = FALSE)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
#### Children All-5 score percentage
## Calculating percentage of each child All-5 score

all_5_percentage <- Selected_Child_indicators %>%
  filter(have_child == 1,breastfed == 0) %>%
  group_by(all_5) %>% 
  summarise(frequency = n()) %>%
  mutate (percentage = round(frequency / sum(frequency)*100))
# print(all_5_percentage)
```


```{r echo=FALSE, message=FALSE, warning=FALSE}
####  Presenting the percentage of children consuming a specific food group
## The percentage of children consuming a specific food group

specific_all_5_group <-Selected_Child_indicators %>% 
  filter(have_child == 1,breastfed == 0) %>%
  select(starchy_staple,Vegetables,fruits,pulses,protein) %>% 
  summarise(round(across(everything(),~ mean(.==1) *100))) %>% 
  pivot_longer(cols = everything(), names_to = "Food Group", values_to = "Percentage")
# print(specific_all_5_group)

```

```{r echo=FALSE, message=FALSE, warning=FALSE}
#### Presenting percentage and graph of Child GDR score for the population
gdr_percentage <- Selected_Child_indicators %>% 
  filter(have_child == 1,breastfed == 0) %>%
  group_by(gdr_score) %>% 
  summarise(Count = n()) %>% 
  mutate(Percentage = round((Count / sum(Count)) * 100))

```

```{r echo=FALSE, message=FALSE, warning=FALSE}
#### Displaying mean of various adult indicator score
Selected_adult_indicators <- Mangwana_Baseline_Survey %>%
  select(formid,form.Section_II_group.ontem_comeu_algum_dos_seguintes_alimentos,form.Section_II_group.comeu_algum_dos_seguintes_alimentos,form.Section_II_group.ontem_comeu_alguma_das_seguintes_frutas,
         form.Section_II_group.ontem_comeu_algum_dos_seguintes_doces,form.Section_II_group.ontem_comeu_algum_dos_seguintes_alimentos_de_origem_animal,
         form.Section_II_group.ontem_comeu_algum_dos_seguintes_outros_alimentos,form.Section_II_group.ontem_tomou_alguma_das_seguintes_bebidas,form.Section_II_group.ontem_conseguiu_comida_em_algum_lugar_como) %>% 
  
  rename(carbohydrate = form.Section_II_group.ontem_comeu_algum_dos_seguintes_alimentos,
         vegetables = form.Section_II_group.comeu_algum_dos_seguintes_alimentos,
         fruits = form.Section_II_group.ontem_comeu_alguma_das_seguintes_frutas,
         sweets_adult = form.Section_II_group.ontem_comeu_algum_dos_seguintes_doces,
         animal_protein = form.Section_II_group.ontem_comeu_algum_dos_seguintes_alimentos_de_origem_animal,
         other_foods = form.Section_II_group.ontem_comeu_algum_dos_seguintes_outros_alimentos,
         drinks = form.Section_II_group.ontem_tomou_alguma_das_seguintes_bebidas,
         fast_food = form.Section_II_group.ontem_conseguiu_comida_em_algum_lugar_como) %>% 
  
  mutate(grains = ifelse(grepl("arroz_po_massa_esparguete_xima_de_farinha_de_milho_processada_papas_de_fari|xima_ou_papas_de_milho_no_processado_mexoeira_mapira_maaroca_po_integral_ou|batata_batata_doce_branca_inhame_mandioca_xima_de_mandioca_ou_papas_de_mand",
                               carbohydrate),1,0), # Classified processed and whole grain crops, tubers, porridge
         pulses = ifelse(grepl("mangwana_forms_mangwana_forms_100_10_d264_feijo_feijo_nhemba_ervilha_feijo_", carbohydrate),1,0), # Classified beans, cowpea, peas, pigeon peas
         nuts = ifelse(grepl("amendoim_manteiga_de_amendoim_amendoim_modo_castanhas_de_caj_ou_sementes_de",other_foods),1,0), # Classified nuts and seeds
         diary = ifelse(grepl("leite_fresco_ou_leite_em_p",drinks),1,0), # Classified animal milk
         meat_fish = ifelse(grepl("paloni_salsichas_ou_enchidos_como_chourio_linguia_rachel_russian_ou_vorse|carne_de_vaca_carne_de_cabrito_fgado_carne_de_ovelha_gazela_ou_bufalo|
                                    carne_de_porco_carne_de_ratazana_ou_coelho|galinha_moela_pato_peru_codorniz_ou_passarinhos|
                                    peixe_fresco_ou_seco_camaro_fresco_ou_seco_caranguejo_lulas_ou_ameijoa", animal_protein),1,0), # Animal protein
         diary_product = ifelse(grepl("queijo|iogurte",animal_protein),1,0), # diary product
         dark_leafy_veg = ifelse(grepl("couve_folhas_de_abobora_folhas_de_cacana_folhas_de_batata_doce_folha_de_fei|brculos_espinafres_folhas_de_moringa_folhas_de_amaranto_ou_quiabo_de_folha", vegetables),1,0), # Dark leafy green vegetables
         egg = ifelse(grepl("ovos",animal_protein),1,0), # Egg
         vitamin_A_veg = ifelse(grepl("cenoura_abbora_ou_batata_doce_de_polpa_alaranjada|tomate_repolho_quiabo_beringela_ou_cogumelos|alface_pepino_feijo_verde_ou_pimento_verde", vegetables),1,0), # Vitamin A rich vegetables
         vitamin_A_orange_veg = ifelse(grepl("cenoura_abbora_ou_batata_doce_de_polpa_alaranjada", vegetables),1,0), # Vitamin A orange vegetables
         vitamin_A_fruit = ifelse(grepl("manga_papaia_ou_maracuj|laranja_ou_tangerinas|ma_pra_goiaba_massala_ata_mapfilo_tintsiva_ou_mafurra", fruits),1,0), # Vitamin A rich fruits
         other_fruit = ifelse(grepl("bananas_melancia_abacate_lichia_caju_anans_ou_malambe", fruits),1,0), # Other fruits
         whole_grain = ifelse(grepl("xima_ou_papas_de_milho_no_processado_mexoeira_mapira_maaroca_po_integral_ou",
                                    carbohydrate),1,0), # Classified whole grain crops
         citrus_fruit = ifelse(grepl("laranja_ou_tangerinas", fruits),1,0), # Citrus fruits
         soft_drink = ifelse(grepl("refrescos_como_coca-cola_fanta_frozy_ou_fizz_ou_bebidas_energticas_como_o_r|sumos_ou_sumos_em_p|ch_com_acucar_caf_com_acucar_ou_achocolatado_como_milo", drinks),1,0), # Soft drinks
         sweet_snacks = ifelse(grepl("chips_pipocas_de_pacote_ou_niknaks", other_foods),1,0), # snack-based sweets
         adult_sweet = ifelse(grepl("bolos_bolinhos_bolachas_doces_argolas_fritas_bolas_de_berlim_ou_fiosso|chupa_chupa_ou_doces_bombom_chocolate_sorvete_ou_gelinho", sweets_adult),1,0), # Baked and other sweets
         processed_meat = ifelse(grepl("paloni_salsichas_ou_enchidos_como_chourio_linguia_rachel_russian_ou_vorse", animal_protein),1,0), # Processed meat
         unprocessed_meat = ifelse(grepl("carne_de_vaca_carne_de_cabrito_fgado_carne_de_ovelha_gazela_ou_bufalo|carne_de_porco_carne_de_ratazana_ou_coelho|
                                    galinha_moela_pato_peru_codorniz_ou_passarinhos", animal_protein),1,0), # Unprocessed meat
         deep_fried_food = ifelse(grepl("peixe_fresco_ou_seco_camaro_fresco_ou_seco_caranguejo_lulas_ou_ameijoa", animal_protein),1,0), # Deep fried foods
         fast_food = ifelse(grepl("refrescos_como_coca-cola_fanta_frozy_ou_fizz_ou_bebidas_energticas_como_o_r", fast_food),1,0), # Fast foods
         
         ## Dietary Diversity Score for the entire adult population
         adult_dds = (rowSums(tibble(grains)==1) >0) +
           (rowSums(tibble(pulses)==1) >0) +
           (rowSums(tibble(nuts)==1) >0) + 
           (rowSums(tibble(diary)==1) >0) +
           (rowSums(tibble(meat_fish)==1) >0) +
           (rowSums(tibble(dark_leafy_veg)==1) >0) +
           (rowSums(tibble(egg)==1) >0) +
           (rowSums(tibble(vitamin_A_veg,vitamin_A_fruit)==1) >0) +
           (rowSums(tibble(other_fruit)==1) >0),
         adult_all_5 = (rowSums(tibble(grains)==1) >0) +
           (rowSums(tibble(dark_leafy_veg,vitamin_A_veg)==1) >0) +
           (rowSums(tibble(vitamin_A_fruit,other_fruit)==1) >0) + 
           (rowSums(tibble(nuts)==1) >0) +
           (rowSums(tibble(meat_fish)==1) >0),
         adult_ncd_protect = (rowSums(tibble(whole_grain)==1) >0) +
           (rowSums(tibble(nuts)==1) >0) +
           (rowSums(tibble(citrus_fruit)==1) >0) +
           (rowSums(tibble(vitamin_A_veg)==1) >0) + 
           (rowSums(tibble(dark_leafy_veg)==1) >0) +
           (rowSums(tibble(vitamin_A_fruit)==1) >0) +
           (rowSums(tibble(other_fruit)==1) >0),
         adult_ncd_risk = (rowSums(tibble(soft_drink)==1) >0) +
           (rowSums(tibble(sweet_snacks)==1) >0) +
           (rowSums(tibble(adult_sweet)==1) >0) +
           2 * (rowSums(tibble(processed_meat)==1) >0) +
           (rowSums(tibble(unprocessed_meat)==1) >0) +
           (rowSums(tibble(deep_fried_food)==1) >0) +
           (rowSums(tibble(fast_food)==1) >0),
         ## Calculating binaries and gdr score for adult population
         adult_dss_binary =  ifelse(adult_dds >= 5, 1,0),
         adult_all_5_binary = ifelse(adult_all_5 == 5, 1,0),
         adult_ncd_protect_binary = ifelse(adult_ncd_protect >= 5, 1,0),
         adult_ncd_risk_binary = ifelse(adult_ncd_risk>= 5, 1,0),
         adult_gdr_score = (adult_ncd_protect - adult_ncd_risk) + 9, #Calculating General Dietary Recommendation (GDR score)
         ## Calculating various all 5 food groups for a graph
         carbs = ifelse(!is.na(carbohydrate) & carbohydrate != "",1,0),
         fruit = ifelse(!is.na(fruits) & fruits != "",1,0),
         vegetable = ifelse(!is.na(vegetables) & vegetables != "",1,0),
         proteins = ifelse(!is.na(animal_protein) & animal_protein != "",1,0),
         pulse = if_else(rowSums(across(c(pulses,nuts)) == 1) > 0, 1, 0))
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
#### Displaying updated data and calculating means of various scores for adult population
avg_dds_score <- round(mean(Selected_adult_indicators$adult_dds),1) # Calculating the average DDS score for the entire population

avg_all_5_score <- round(mean(Selected_adult_indicators$adult_all_5),1) # Calculating the average All 5 score for the entire population

avg_ncd_protect_score <- round(mean(Selected_adult_indicators$adult_ncd_protect),1) # Calculating the average NCD protect score for the entire population

avg_ncd_risk_score <- round(mean(Selected_adult_indicators$adult_ncd_risk),1) # Calculating the average NCD risk score for the entire population

avg_gdr_score <- round(mean(Selected_adult_indicators$adult_gdr_score),1) # Calculating the average GDR score for the entire population
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
### Calculating the various percentages and graphs of adult indicators.

#### Presenting percentages of adult DDS
adult_dds_percentage <- Selected_adult_indicators %>%
  group_by(adult_dds) %>% 
  summarise(dds_count = n()) %>%
  mutate (percentage = round(dds_count / sum(dds_count)*100))
# print(adult_dds_percentage)
```


```{r echo=FALSE, message=FALSE, warning=FALSE}
### Selecting indicators for Resilience to shocks
Resilience <- Mangwana_Baseline_Survey %>% 
  select(formid, form.Section_III_group.missed_food, form.Section_III_group.Months_missed_food, form.Section_III_group.you_feared_HH_not_have_enough_food,form.Section_III_group.how_may_times_HH_not_have_enough_food,
         form.Section_III_group.not_enough_food,form.Section_III_group.how_many_times_not_enough_food, form.Section_III_group.all_day_night_not_eating, form.Section_III_group.how_many_times_all_day_night_not_eating) %>% # Selected indicators of interest
  
  mutate(
    MAHFP = 12 - sapply(strsplit(ifelse(form.Section_III_group.Months_missed_food == "---","",form.Section_III_group.Months_missed_food)," "), length), # Calculated the months of adequate food
    across(c(form.Section_III_group.how_may_times_HH_not_have_enough_food, form.Section_III_group.how_many_times_not_enough_food,form.Section_III_group.how_many_times_all_day_night_not_eating), ~ case_when(. %in% c("Sometimes", "Rarely") ~ 1, . == "---" ~ 0, . == "Frequently" ~ 2)), # Replaced three category indicators with integers
    hhs_score = form.Section_III_group.how_may_times_HH_not_have_enough_food + form.Section_III_group.how_many_times_not_enough_food + form.Section_III_group.how_many_times_all_day_night_not_eating,
    hunger_scores = case_when(hhs_score <= 1 ~ "Little to no hunger",
                              hhs_score <= 3 ~ "Moderate hunger",
                              hhs_score <=6 ~ "Severe hunger") # Classified the household hunger scores from little to severe. 
    
  ) 


MAHFP_months <- Resilience %>% 
  select(form.Section_III_group.Months_missed_food) %>% 
  mutate(months = na_if(form.Section_III_group.Months_missed_food, "---"),
         months = str_to_title(months)) %>%
  drop_na() %>% 
  separate_rows(months, sep = " ") %>% 
  count(months)
MAHFP_months$months <- factor(MAHFP_months$months,
                               levels = month.name)

Average_MAHFP <- round(mean(Resilience$MAHFP),1) # Average months households had adequate food.
# print(paste("Average MAHFP for the population is", Average_MAHFP))

Median_hhs_score <- median(Resilience$hhs_score) # Median value of HHS score
#  print(paste("Median HHS score for the population is", Median_hhs_score))

```


```{r echo=FALSE, message=FALSE, warning=FALSE}
#### Percentage of HHS scores
HHS_percentage <- Resilience %>% 
  group_by(hunger_scores) %>% 
  summarise(Count = n()) %>% 
  mutate(Percentage = round((Count / sum(Count)) * 100))
# print(HHS_percentage)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
#### Additional calculations for MAHFP follow up
## Arranging the MAHFP for follow up

MAHFP_resilience <- Resilience %>%
  select(MAHFP) %>% 
  arrange(MAHFP) 
MAHFP_num <- nrow(MAHFP_resilience)
MAHFP_number <- ceiling(MAHFP_num / 3)
top_third <- MAHFP_resilience %>% 
  slice((MAHFP_num -  MAHFP_number + 1): MAHFP_num) 
mean_top_third <- mean(top_third$MAHFP)

```

```{r echo=FALSE, message=FALSE, warning=FALSE}
## Agriculture indicators.

### Baseline dry season crops
## Merging the general data sheet and the repeat agriculture sheet to filter to baseline data

## Importing baseline dry season dataset

## Selecting only baseline season records to be used for agricultural calculations

Baseline_drought_data <- Mangwana_Baseline_Survey %>%
  filter(form.Section_IV_ProductionAreas.que_tipo_de_inqurito_est_a_realizar == "inqurito_de_base_para_as_duas_ltimas_pocas")


Drought_repeat_Survey <- read_excel("Mangwana - Baseline Survey.xlsx",
                                    sheet = "BL_dryseason_crops")


Mangwana_Baseline_Survey <- read_excel("Mangwana - Baseline Survey.xlsx", 
                                       sheet = "Forms")

## Constant variables
number_dryseason_weeks <- 23
number_rainy_season_weeks <- 29 ## Confirm this from team
Standard_workhours <- 8
PPP <- 24.95 ## Current (2025) PPP. Source: https://www.imf.org/external/datamapper/PPPEX@WEO/MOZ?zoom=MOZ&highlight=MOZ

## Data manipulation

extract_kg <- function(unit_measure) {
  unit_measure <- tolower(trimws(unit_measure))
  if (unit_measure == "other_unit_measure_baseline_rainseason") {
    return(20)
  }
  if (str_detect(unit_measure, "quilo")) {
    return(1)
  }
  matches <- str_match_all(unit_measure, "(\\d+)(?=[_=]?kg)")[[1]]
  if (nrow(matches) > 0) {
    return(as.numeric(tail(matches[, 1], 1)))
  }
  return(NA_real_)
}


Baseline_drought <- Drought_repeat_Survey %>%
  
  
  inner_join(Mangwana_Baseline_Survey %>%  select(formid,form.Section_IV_ProductionAreas.que_tipo_de_inqurito_est_a_realizar), by = c("formid" = "formid")) %>% 
  
  filter(form.Section_IV_ProductionAreas.que_tipo_de_inqurito_est_a_realizar == "inqurito_de_base_para_as_duas_ltimas_pocas") %>% 
  
  mutate(across(everything(), ~ case_when(. == "---" ~ "0",
                                          . == " " ~ "0",
                                          is.na(.) ~ "0",
                                          TRUE ~ as.character(.)))) %>% 
  
  rename(qty_crops_produced = form.Section_IV_ProductionAreas.baseline_dryseason_questions.repeat_baseline_dryseason_crops.qty_baseline_produced_dry_season,
         cropland_ha = form.Section_IV_ProductionAreas.baseline_dryseason_questions.repeat_baseline_dryseason_crops.baseline_cropland_dryseason,
         days_per_week_fieldwork = form.Section_IV_ProductionAreas.baseline_dryseason_questions.repeat_baseline_dryseason_crops.days_of_work_dryseason_baseline,
         hours_per_day_fieldwork = form.Section_IV_ProductionAreas.baseline_dryseason_questions.repeat_baseline_dryseason_crops.hours_of_work_dryseason_baseline,
         number_family_labour = form.Section_IV_ProductionAreas.baseline_dryseason_questions.repeat_baseline_dryseason_crops.number_farm_assisatnce_baseline,
         assist_days_perweek_fieldwork = form.Section_IV_ProductionAreas.baseline_dryseason_questions.repeat_baseline_dryseason_crops.baseline_farm_assist_days,
         assist_hoursper_fieldwork = form.Section_IV_ProductionAreas.baseline_dryseason_questions.repeat_baseline_dryseason_crops.baseline_farm_assist_hours, 
         number_paid_labour = form.Section_IV_ProductionAreas.baseline_dryseason_questions.repeat_baseline_dryseason_crops.seasonal_hiredworkers_baseline,
         paidlabour_days_perweek_fieldwork = form.Section_IV_ProductionAreas.baseline_dryseason_questions.repeat_baseline_dryseason_crops.days_of_hiredwork_dryseason_baseline,
         paidlabour_hours_per_fieldwork = form.Section_IV_ProductionAreas.baseline_dryseason_questions.repeat_baseline_dryseason_crops.hours_of_hiredwork_dryseason_baseline,
         qty_crops_sold = form.Section_IV_ProductionAreas.baseline_dryseason_questions.repeat_baseline_dryseason_crops.qty_sold_dryseason_baseline,
         price_per_unit_sold = form.Section_IV_ProductionAreas.baseline_dryseason_questions.repeat_baseline_dryseason_crops.price_sold_dryseason_baseline,
         seed_expense = form.Section_IV_ProductionAreas.baseline_dryseason_questions.repeat_baseline_dryseason_crops.expense_on_seeds_dry_season_baseline,
         equipment_expense = form.Section_IV_ProductionAreas.baseline_dryseason_questions.repeat_baseline_dryseason_crops.expense_on_equipment_dry_season_baseline,
         fert_expense = form.Section_IV_ProductionAreas.baseline_dryseason_questions.repeat_baseline_dryseason_crops.expense_on_fert_dry_season_baseline,
         labour_expense = form.Section_IV_ProductionAreas.baseline_dryseason_questions.repeat_baseline_dryseason_crops.expense_on_labor_dry_season_baseline,
         other_expense = form.Section_IV_ProductionAreas.baseline_dryseason_questions.repeat_baseline_dryseason_crops.expense_on_other_dry_season_baseline,
         pesticide_expense = form.Section_IV_ProductionAreas.baseline_dryseason_questions.repeat_baseline_dryseason_crops.expense_on_pesticidas_dry_season_baseline) %>% 
  
  mutate(across(c(qty_crops_produced, cropland_ha, days_per_week_fieldwork, hours_per_day_fieldwork, assist_days_perweek_fieldwork, assist_hoursper_fieldwork, paidlabour_days_perweek_fieldwork,
                  paidlabour_hours_per_fieldwork,qty_crops_sold,price_per_unit_sold, number_paid_labour, number_family_labour, seed_expense,equipment_expense, fert_expense,labour_expense,other_expense,pesticide_expense), as.numeric)) %>% 
  
  ## Calculating  Labour days and productivity 
  
  mutate(total_weeks_fieldwork = rowSums(across(c(days_per_week_fieldwork,assist_days_perweek_fieldwork,paidlabour_days_perweek_fieldwork))),
         dry_unit_kg = sapply(form.Section_IV_ProductionAreas.baseline_dryseason_questions.repeat_baseline_dryseason_crops.unit_measure_produce_dry_season_baseline, extract_kg),
         qty_prod_kg = ifelse(is.na(dry_unit_kg), 0,qty_crops_produced * dry_unit_kg),
         personallabour_time= days_per_week_fieldwork*hours_per_day_fieldwork,
         assistedlabour_time = assist_days_perweek_fieldwork * assist_hoursper_fieldwork*number_family_labour,
         paidlabour_time = paidlabour_days_perweek_fieldwork * paidlabour_hours_per_fieldwork*number_paid_labour,
         personallabour_days = (personallabour_time*number_dryseason_weeks)/Standard_workhours,
         assistedlabour_days = (assistedlabour_time*number_dryseason_weeks)/Standard_workhours,
         paidlabour_days = (paidlabour_time*number_dryseason_weeks)/Standard_workhours,
         total_labour_days = rowSums(across(c(personallabour_days, assistedlabour_days, paidlabour_days))),
         drysale_unit_kg = sapply(form.Section_IV_ProductionAreas.baseline_dryseason_questions.repeat_baseline_dryseason_crops.unit_measure_baseline_sold_dryseason, extract_kg),
         qty_sold_kg = ifelse(is.na(drysale_unit_kg),0,qty_crops_produced * drysale_unit_kg),
         crops_income = qty_sold_kg*price_per_unit_sold,
         productivity = (qty_prod_kg*price_per_unit_sold)/total_labour_days,
         total_expense = rowSums(across(c(seed_expense,pesticide_expense,fert_expense,equipment_expense,other_expense,labour_expense))),
         crop_yield = qty_prod_kg/cropland_ha,
         gross_agric_income = crops_income - total_expense)

## Productivity

total_crop_income <-sum(Baseline_drought$crops_income)
# print(paste("Total dry season income for the population is", total_crop_income))

## Agriculture gross income

agric_gross <- sum(Baseline_drought$gross_agric_income)
# print(paste("Total dry season gross income for the population is", agric_gross))

## Grouping data for merging
Baseline_drought_grouped <- Baseline_drought %>% 
  select(qty_sold_kg,price_per_unit_sold, qty_prod_kg, cropland_ha, formid, personallabour_time,assistedlabour_time,personallabour_days,assistedlabour_days,paidlabour_days,
         total_labour_days, crops_income,productivity,total_expense,crop_yield,gross_agric_income) %>% 
  group_by(formid) %>%
  summarise(across(where(is.numeric),  \(x) sum(x, na.rm = TRUE)), .groups = "drop")

```

```{r echo=FALSE, message=FALSE, warning=FALSE}
### Baseline rainy season crops
Rainy_repeat_Survey <- read_excel("Mangwana - Baseline Survey.xlsx",
                                  sheet = "BL_rainseason_crops")


Baseline_rainy <- Rainy_repeat_Survey %>%
  
  
  inner_join(Mangwana_Baseline_Survey %>%  select(formid,form.Section_IV_ProductionAreas.que_tipo_de_inqurito_est_a_realizar), by = c("formid" = "formid")) %>% 
  
  filter(form.Section_IV_ProductionAreas.que_tipo_de_inqurito_est_a_realizar == "inqurito_de_base_para_as_duas_ltimas_pocas") %>% 
  
  mutate(across(everything(), ~ case_when(. == "---" ~ "0",
                                          . == " " ~ "0",
                                          is.na(.) ~ "0",
                                          TRUE ~ as.character(.)))) %>% 
  
  rename(rainy_qty_crops_produced = form.Section_IV_ProductionAreas.baseline_rainy_season_questions.repeat_baseline_rainseason_crops.qty_baseline_produced_rain_season,
         rainy_cropland_ha = form.Section_IV_ProductionAreas.baseline_rainy_season_questions.repeat_baseline_rainseason_crops.baseline_cropland_rainseason,
         rainy_days_per_week_fieldwork = form.Section_IV_ProductionAreas.baseline_rainy_season_questions.repeat_baseline_rainseason_crops.days_of_work_rainseason_baseline,
         rainy_hours_per_day_fieldwork = form.Section_IV_ProductionAreas.baseline_rainy_season_questions.repeat_baseline_rainseason_crops.hours_of_work_rainseason_baseline,
         rainy_number_family_labour = form.Section_IV_ProductionAreas.baseline_rainy_season_questions.repeat_baseline_rainseason_crops.number_farm_assisatnce_baseline_rain,
         rainy_assist_days_perweek_fieldwork = form.Section_IV_ProductionAreas.baseline_rainy_season_questions.repeat_baseline_rainseason_crops.baseline_farm_assist_days_rain,
         rainy_assist_hoursper_fieldwork = form.Section_IV_ProductionAreas.baseline_rainy_season_questions.repeat_baseline_rainseason_crops.baseline_farm_assist_hours_rain, 
         rainy_number_paid_labour = form.Section_IV_ProductionAreas.baseline_rainy_season_questions.repeat_baseline_rainseason_crops.seasonal_hiredworkers_baseline_rain,
         rainy_paidlabour_days_perweek_fieldwork = form.Section_IV_ProductionAreas.baseline_rainy_season_questions.repeat_baseline_rainseason_crops.days_of_hiredwork_rainseason_baseline,
         rainy_paidlabour_hours_per_fieldwork = form.Section_IV_ProductionAreas.baseline_rainy_season_questions.repeat_baseline_rainseason_crops.hours_of_hiredwork_rainseason_baseline,
         rainy_qty_crops_sold = form.Section_IV_ProductionAreas.baseline_rainy_season_questions.repeat_baseline_rainseason_crops.qty_sold_rainyseason_baseline,
         rainy_price_per_unit_sold = form.Section_IV_ProductionAreas.baseline_rainy_season_questions.repeat_baseline_rainseason_crops.price_sold_dryseason_baseline,
         rainy_seed_expense = form.Section_IV_ProductionAreas.baseline_rainy_season_questions.repeat_baseline_rainseason_crops.expense_on_seeds_rain_season_baseline,
         rainy_equipment_expense = form.Section_IV_ProductionAreas.baseline_rainy_season_questions.repeat_baseline_rainseason_crops.expense_on_equipment_rain_season_baseline,
         rainy_fert_expense = form.Section_IV_ProductionAreas.baseline_rainy_season_questions.repeat_baseline_rainseason_crops.expense_on_fert_rain_season_baseline,
         rainy_labour_expense = form.Section_IV_ProductionAreas.baseline_rainy_season_questions.repeat_baseline_rainseason_crops.expense_on_labor_rain_season_baseline,
         rainy_other_expense = form.Section_IV_ProductionAreas.baseline_rainy_season_questions.repeat_baseline_rainseason_crops.expense_on_other_rain_season_baseline,
         rainy_pesticide_expense = form.Section_IV_ProductionAreas.baseline_rainy_season_questions.repeat_baseline_rainseason_crops.expense_on_pesticidas_rain_season_baseline) %>% 
  
  mutate(across(c(rainy_qty_crops_produced, rainy_cropland_ha, rainy_qty_crops_sold, rainy_number_family_labour,rainy_number_paid_labour,rainy_days_per_week_fieldwork, rainy_hours_per_day_fieldwork, rainy_assist_days_perweek_fieldwork, rainy_assist_hoursper_fieldwork, rainy_paidlabour_days_perweek_fieldwork,
                  rainy_paidlabour_hours_per_fieldwork,rainy_price_per_unit_sold, rainy_seed_expense,rainy_equipment_expense, rainy_fert_expense,rainy_labour_expense,rainy_other_expense,rainy_pesticide_expense), as.numeric)) %>% 
  
  ## Calculating  Labour days and productivity for the rainy season
  
  mutate(rainy_total_weeks_fieldwork = rowSums(across(c(rainy_days_per_week_fieldwork,rainy_assist_days_perweek_fieldwork,rainy_paidlabour_days_perweek_fieldwork))),
         unit_kg = sapply(form.Section_IV_ProductionAreas.baseline_rainy_season_questions.repeat_baseline_rainseason_crops.unit_measure_produce_rain_season_baseline, extract_kg),
         rainy_qty_prod_kg = ifelse(is.na(unit_kg),0,rainy_qty_crops_produced * unit_kg),
         rainy_personallabour_time= rainy_days_per_week_fieldwork*rainy_hours_per_day_fieldwork,
         rainy_assistedlabour_time = rainy_assist_days_perweek_fieldwork * rainy_assist_hoursper_fieldwork*rainy_number_family_labour,
         rainy_paidlabour_time = rainy_paidlabour_days_perweek_fieldwork * rainy_paidlabour_hours_per_fieldwork*rainy_number_paid_labour,
         rainy_personallabour_days = (rainy_personallabour_time*number_rainy_season_weeks)/Standard_workhours,
         rainy_assistedlabour_days = (rainy_assistedlabour_time*number_rainy_season_weeks)/Standard_workhours,
         rainy_paidlabour_days = (rainy_paidlabour_time*number_rainy_season_weeks)/Standard_workhours,
         rainy_total_labour_days = rowSums(across(c(rainy_personallabour_days, rainy_assistedlabour_days, rainy_paidlabour_days))),
         sale_unit_kg = sapply(form.Section_IV_ProductionAreas.baseline_rainy_season_questions.repeat_baseline_rainseason_crops.unit_measure_baseline_sold_rainseason, extract_kg),
         rainy_qty_sold_kg = ifelse(is.na(sale_unit_kg),0,rainy_qty_crops_sold * sale_unit_kg),
         rainy_crops_income = rainy_qty_sold_kg*rainy_price_per_unit_sold,
         rainy_productivity = (rainy_qty_prod_kg*rainy_price_per_unit_sold)/rainy_total_labour_days,
         rainy_total_expense = rowSums(across(c(rainy_seed_expense,rainy_pesticide_expense,rainy_fert_expense,rainy_equipment_expense,rainy_other_expense,rainy_labour_expense))),
         rainy_crop_yield = rainy_qty_prod_kg/rainy_cropland_ha,
         rainy_gross_agric_income = rainy_crops_income - rainy_total_expense)

## Productivity in rainy season

total_rainy_crop_income <-sum(Baseline_rainy$rainy_crops_income)
# print(paste("Total rainy season income for the population is", total_rainy_crop_income))

## Agriculture gross income in rainy season

agric_gross_rainseason <- sum(Baseline_rainy$rainy_gross_agric_income)
# print(paste("Total rainy season gross income for the population is", agric_gross_rainseason))

## Grouping data for merging
Baseline_rainy_grouped <- Baseline_rainy %>% 
  select(rainy_qty_sold_kg, rainy_price_per_unit_sold, rainy_qty_prod_kg, rainy_cropland_ha, formid, rainy_total_weeks_fieldwork,rainy_personallabour_time, rainy_assistedlabour_time, rainy_paidlabour_time, rainy_personallabour_days,
         rainy_assistedlabour_days,rainy_paidlabour_days,rainy_total_labour_days, rainy_crops_income, rainy_productivity, rainy_total_expense,
         rainy_crop_yield, rainy_gross_agric_income) %>% 
  group_by(formid) %>%
  summarise(across(where(is.numeric),  \(x) sum(x, na.rm = TRUE)), .groups = "drop")
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
### Agroforestry indicators
## Importing data

Agroforestry_repeat_Survey <- read_excel("Mangwana - Baseline Survey.xlsx", 
                                         sheet = "Repeat- product_silviculture")

## Selecting a subset of data 
Baseline_drought_agroforestry <- Agroforestry_repeat_Survey %>% 
  
  
  
  inner_join(Mangwana_Baseline_Survey %>%  select(formid,form.Section_IV_ProductionAreas.que_tipo_de_inqurito_est_a_realizar), by = c("formid" = "formid")) %>% 
  
  filter(form.Section_IV_ProductionAreas.que_tipo_de_inqurito_est_a_realizar == "inqurito_de_base_para_as_duas_ltimas_pocas") %>% 
  
  mutate(across(everything(), ~ case_when(. == "---" ~ "0",
                                          . == " " ~ "0",
                                          is.na(.) ~ "0",
                                          TRUE ~ as.character(.)))) %>% 
  
  rename(agro_sale_price = form.Section_IV_ProductionAreas.Section_IV_III_Silviculture.product_silviculture.sale_price_silviculture,
         agro_crops_produced = form.Section_IV_ProductionAreas.Section_IV_III_Silviculture.product_silviculture.que_quantidade_de_produto_em_unidade_de_medida_produziu_na_ltima_poca,
         agro_crop_ha = form.Section_IV_ProductionAreas.Section_IV_III_Silviculture.product_silviculture.land_production_silviculture,
         agro_qty_sold = form.Section_IV_ProductionAreas.Section_IV_III_Silviculture.product_silviculture.qty_sold_silviculture,
         seed_cost = form.Section_IV_ProductionAreas.Section_IV_III_Silviculture.product_silviculture.expenditures_sementes_silviculture,
         pesticide_cost = form.Section_IV_ProductionAreas.Section_IV_III_Silviculture.product_silviculture.expenditures_pesticidas_silviculture,
         fert_cost = form.Section_IV_ProductionAreas.Section_IV_III_Silviculture.product_silviculture.expenditures_fertilizantes_silviculture,
         labour_cost = form.Section_IV_ProductionAreas.Section_IV_III_Silviculture.product_silviculture.expenditures_labor_silviculture,
         equipment_expense = form.Section_IV_ProductionAreas.Section_IV_III_Silviculture.product_silviculture.expenditures_equipment_silviculture,
         other_expense = form.Section_IV_ProductionAreas.Section_IV_III_Silviculture.product_silviculture.expenditures_other_silviculture,
         forest_daysperweek_work = form.Section_IV_ProductionAreas.Section_IV_III_Silviculture.product_silviculture.quantos_dias_por_semana_voc_trabalhou_para_silvicultura,
         forest_hoursperweek_work = form.Section_IV_ProductionAreas.Section_IV_III_Silviculture.product_silviculture.quantas_horas_por_dia_voc_trabalhou_para_silvicultura,
         forest_number_family_labour = form.Section_IV_ProductionAreas.Section_IV_III_Silviculture.product_silviculture.quantos_membros_da_famlia_ajudaram_voc_se_aplicvel_tambm_inclua_seu_parceir,
         forest_assist_daysperweek_work = form.Section_IV_ProductionAreas.Section_IV_III_Silviculture.product_silviculture.em_mdia_quantos_dias_por_semana_eles_ajudaram_voc,
         forest_number_permanent_labour = form.Section_IV_ProductionAreas.Section_IV_III_Silviculture.product_silviculture.quantos_trabalhadores_permanente_voc_contratou,
         forest_permanent_hoursperweek_work = form.Section_IV_ProductionAreas.Section_IV_III_Silviculture.product_silviculture.em_mdia_quantas_horas_por_dia_eles_trabalharam_para_voc,
         forest_permanent_daysperweek_work = form.Section_IV_ProductionAreas.Section_IV_III_Silviculture.product_silviculture.em_mdia_por_quantos_dias_por_semana_voc_os_contratou,
         forest_number_seasonal_labour = form.Section_IV_ProductionAreas.Section_IV_III_Silviculture.product_silviculture.quantos_trabalhadores_sazonais_voc_contratou,
         forest_seasonal_daysperweek_work = `form.Section_IV_ProductionAreas.Section_IV_III_Silviculture.product_silviculture.copy-1-of-em_mdia_por_quantos_dias_por_semana_voc_os_contratou`) %>% 
  
  mutate(across(c(agro_crop_ha,agro_sale_price,agro_crops_produced,agro_qty_sold,seed_cost,forest_number_family_labour,forest_number_permanent_labour,forest_number_seasonal_labour, pesticide_cost,fert_cost,labour_cost,equipment_expense,other_expense,forest_daysperweek_work,
                  forest_hoursperweek_work,forest_permanent_hoursperweek_work,forest_permanent_daysperweek_work,forest_seasonal_daysperweek_work,forest_assist_daysperweek_work),as.numeric)) %>% 
  
  # Calculating productivity and gross income for Agroforestry
  mutate(agro_unit_kg = sapply(form.Section_IV_ProductionAreas.Section_IV_III_Silviculture.product_silviculture.unit_measure_production_silviculture, extract_kg),
         agro_qty_prod_kg = ifelse(is.na(agro_unit_kg),0,agro_crops_produced * agro_unit_kg),
         agrosale_unit_kg = sapply(form.Section_IV_ProductionAreas.Section_IV_III_Silviculture.product_silviculture.unit_measure_sale_silviculture, extract_kg),
         agro_qty_sold_kg = ifelse(is.na(agrosale_unit_kg),0,agro_qty_sold * agrosale_unit_kg),
    forest_crop_income = agro_sale_price * agro_qty_sold_kg,
         forest_total_expenses = rowSums(across(c(seed_cost,pesticide_cost,fert_cost,labour_cost,equipment_expense,other_expense))),
         forest_gross_income = forest_crop_income - forest_total_expenses,
         forest_personallabour_time = forest_daysperweek_work*forest_hoursperweek_work,
         forest_assistedlabour_time = forest_assist_daysperweek_work *Standard_workhours* forest_number_family_labour, ## No indicator on hours worked, so I used standard hours
         forest_permantlabr_time = forest_permanent_hoursperweek_work * forest_permanent_daysperweek_work * forest_number_permanent_labour,
         forest_seasonallabr_time = forest_seasonal_daysperweek_work * Standard_workhours*forest_number_seasonal_labour,## No indicator on hours worked, so I used standard hours
         forest_totallabr_days = rowSums(across(c(forest_personallabour_time,forest_assistedlabour_time,forest_permantlabr_time,forest_seasonallabr_time))),
         forest_productivity = ifelse(forest_totallabr_days == 0, 0, (agro_qty_prod_kg * agro_sale_price) / forest_totallabr_days))


## Agroforestry gross income

agroforestry_gross <- sum(Baseline_drought_agroforestry$forest_gross_income)
# print(paste("Gross agroforestry income for the population is", agroforestry_gross))

## Grouping data for merging
Baseline_dry_forestry_grouped <- Baseline_drought_agroforestry %>% 
  select(agro_crop_ha,agro_sale_price, agro_qty_prod_kg, agro_qty_sold_kg, formid, forest_crop_income, forest_total_expenses, forest_gross_income, forest_personallabour_time, forest_assistedlabour_time,
         forest_permantlabr_time, forest_seasonallabr_time, forest_totallabr_days, forest_productivity) %>% 
  group_by(formid) %>%
  summarise(across(where(is.numeric),  \(x) sum(x, na.rm = TRUE)), .groups = "drop")


```

```{r echo=FALSE, message=FALSE, warning=FALSE}
### Livestock indicators
## Importing data

Animal_repeat_Survey <- read_excel("Mangwana - Baseline Survey.xlsx",
                                   sheet = "Repeat- Animals_Raised")

Baseline_drought_animals <- Animal_repeat_Survey %>% 
  
  
  inner_join(Mangwana_Baseline_Survey %>%  select(formid,form.Section_IV_ProductionAreas.que_tipo_de_inqurito_est_a_realizar,form.Section_IV_ProductionAreas.Section_IV_IV_Livestock.quantos_dias_por_semana_voc_trabalhou_na_pecuaria,
                                                  form.Section_IV_ProductionAreas.Section_IV_IV_Livestock.quantas_horas_por_dia_voc_trabalhou_na_pecuaria,form.Section_IV_ProductionAreas.Section_IV_IV_Livestock.question21,
                                                  form.Section_IV_ProductionAreas.Section_IV_IV_Livestock.em_mdia_quantos_dias_por_semana_eles_ajudaram_voc,form.Section_IV_ProductionAreas.Section_IV_IV_Livestock.em_mdia_quantas_horas_por_dia_eles_ajudaram_voc,
                                                  form.Section_IV_ProductionAreas.Section_IV_IV_Livestock.quantos_trabalhadores_permanente_voc_contratou,
                                                  form.Section_IV_ProductionAreas.Section_IV_IV_Livestock.em_mdia_por_quantos_dias_por_semana_voc_os_contratou,`form.Section_IV_ProductionAreas.Section_IV_IV_Livestock.copy-1-of-em_mdia_quantas_horas_por_dia_eles_trabalharam_para_voc`,
                                                  form.Section_IV_ProductionAreas.Section_IV_IV_Livestock.em_mdia_quantas_horas_por_dia_eles_trabalharam_para_voc,form.Section_IV_ProductionAreas.Section_IV_IV_Livestock.quantos_trabalhadores_sazonais_voc_contratou,
                                                  `form.Section_IV_ProductionAreas.Section_IV_IV_Livestock.copy-1-of-em_mdia_por_quantos_dias_por_semana_voc_os_contratou`), by = c("formid" = "formid")) %>% 
  
  filter(form.Section_IV_ProductionAreas.que_tipo_de_inqurito_est_a_realizar == "inqurito_de_base_para_as_duas_ltimas_pocas") %>% 
  
  mutate(across(everything(), ~ case_when(. == "---" ~ "0",
                                          . == " " ~ "0",
                                          is.na(.) ~ "0",
                                          TRUE ~ as.character(.)))) %>%
  
  rename(livestock_qty_sold = form.Section_IV_ProductionAreas.Section_IV_IV_Livestock.Animals_Raised.qty_sale_livestock,
         qty_production_livestock = form.Section_IV_ProductionAreas.Section_IV_IV_Livestock.Animals_Raised.qty_production_livestock,
         price_livestock = form.Section_IV_ProductionAreas.Section_IV_IV_Livestock.Animals_Raised.price_livestock,
         livestock_feeding_expense = form.Section_IV_ProductionAreas.Section_IV_IV_Livestock.Animals_Raised.expenditures_feeding_livestock,
         livestock_labour_expense =  form.Section_IV_ProductionAreas.Section_IV_IV_Livestock.Animals_Raised.expenditures_labor_livestock,
         livestock_medical_expense = form.Section_IV_ProductionAreas.Section_IV_IV_Livestock.Animals_Raised.expenditures_medication_livestock,
         livestock_equipment_expense = form.Section_IV_ProductionAreas.Section_IV_IV_Livestock.Animals_Raised.expenditures_equipment_livestock,
         livestock_maintain_expense = form.Section_IV_ProductionAreas.Section_IV_IV_Livestock.Animals_Raised.expenditures_other_livestock,
         livestock_days_of_work = form.Section_IV_ProductionAreas.Section_IV_IV_Livestock.quantos_dias_por_semana_voc_trabalhou_na_pecuaria,
         livestock_hours_per_day = form.Section_IV_ProductionAreas.Section_IV_IV_Livestock.quantas_horas_por_dia_voc_trabalhou_na_pecuaria,
         livestock_number_assisted_workers = form.Section_IV_ProductionAreas.Section_IV_IV_Livestock.question21,
         livestock_assisted_days_of_work = form.Section_IV_ProductionAreas.Section_IV_IV_Livestock.em_mdia_quantos_dias_por_semana_eles_ajudaram_voc,
         livestock_assisted_hours_of_work = form.Section_IV_ProductionAreas.Section_IV_IV_Livestock.em_mdia_quantas_horas_por_dia_eles_ajudaram_voc,
         livestock_number_permanent_workers = form.Section_IV_ProductionAreas.Section_IV_IV_Livestock.quantos_trabalhadores_permanente_voc_contratou,
         livestock_permanent_days_of_work = form.Section_IV_ProductionAreas.Section_IV_IV_Livestock.em_mdia_por_quantos_dias_por_semana_voc_os_contratou,
         livestock_permanent_hours_of_work = form.Section_IV_ProductionAreas.Section_IV_IV_Livestock.em_mdia_quantas_horas_por_dia_eles_trabalharam_para_voc,
         livestock_number_seasonal_workers = form.Section_IV_ProductionAreas.Section_IV_IV_Livestock.quantos_trabalhadores_sazonais_voc_contratou,
         livestock_seasonal_days_of_work = `form.Section_IV_ProductionAreas.Section_IV_IV_Livestock.copy-1-of-em_mdia_por_quantos_dias_por_semana_voc_os_contratou`,
         livestock_seasonal_hours_of_work = `form.Section_IV_ProductionAreas.Section_IV_IV_Livestock.copy-1-of-em_mdia_quantas_horas_por_dia_eles_trabalharam_para_voc`) %>%
  mutate(across(c(qty_production_livestock, livestock_qty_sold,price_livestock,livestock_feeding_expense, livestock_labour_expense, livestock_medical_expense, livestock_equipment_expense, livestock_maintain_expense,
                  livestock_days_of_work,livestock_hours_per_day,livestock_number_assisted_workers,livestock_assisted_days_of_work,livestock_assisted_hours_of_work,
                  livestock_number_permanent_workers,livestock_permanent_days_of_work,livestock_permanent_hours_of_work,livestock_number_seasonal_workers,
                  livestock_seasonal_days_of_work,livestock_seasonal_hours_of_work), as.numeric),
         ## Calculating productivity and gross income for livestock
         livestock_income = livestock_qty_sold * price_livestock,
         livestock_total_expense = rowSums(across(c(livestock_feeding_expense,livestock_labour_expense, livestock_medical_expense,livestock_equipment_expense, livestock_maintain_expense))),
         gross_livestock_income = livestock_income - livestock_total_expense,
         livestock_personallabour_time = livestock_days_of_work * livestock_hours_per_day,
         livestock_assistedlabour_time = livestock_number_assisted_workers * livestock_assisted_days_of_work * livestock_assisted_hours_of_work,
         livestock_permanentlabour_time = livestock_number_permanent_workers * livestock_permanent_days_of_work * livestock_permanent_hours_of_work,
         livestock_seasonallabour_time = livestock_number_seasonal_workers * livestock_seasonal_days_of_work * livestock_seasonal_hours_of_work,
         total_livestock_labour_time = rowSums(across(c(livestock_personallabour_time,livestock_assistedlabour_time,livestock_permanentlabour_time))),
         livestock_productivity = ifelse(total_livestock_labour_time == 0,0, (qty_production_livestock * livestock_qty_sold) /total_livestock_labour_time))



gross_livestock <- sum(Baseline_drought_animals$livestock_income)
# print(paste("Gross livestock income for the population is", gross_livestock))

## Grouping data for merging
Baseline_dry_animals_grouped <- Baseline_drought_animals %>% 
  select(qty_production_livestock, livestock_qty_sold, price_livestock, formid, livestock_income, livestock_total_expense, gross_livestock_income, livestock_personallabour_time, livestock_assistedlabour_time,
         livestock_permanentlabour_time, livestock_seasonallabour_time, total_livestock_labour_time, livestock_productivity) %>% 
  group_by(formid) %>%
  summarise(across(where(is.numeric),  \(x) sum(x, na.rm = TRUE)), .groups = "drop")
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
### Fish farming
Fish_repeat_Survey <- read_excel("Mangwana - Baseline Survey.xlsx",
                                 sheet = "Repeat- type_fish")


Baseline_drought_fish <- Fish_repeat_Survey %>% 
  
  
  inner_join(Mangwana_Baseline_Survey %>%  select(formid,form.Section_IV_ProductionAreas.que_tipo_de_inqurito_est_a_realizar), by = c("formid" = "formid")) %>% 
  
  filter(form.Section_IV_ProductionAreas.que_tipo_de_inqurito_est_a_realizar == "inqurito_de_base_para_as_duas_ltimas_pocas") %>% 
  
  mutate(across(everything(), ~ case_when(. == "---" ~ "0",
                                          . == " " ~ "0",
                                          is.na(.) ~ "0",
                                          TRUE ~ as.character(.)))) %>%
  
  rename(fish_qty_produced = form.Section_IV_ProductionAreas.Section_IV_V_FishFarming.type_fish.qty_production_Aquaculture,
         fish_qty_sold = form.Section_IV_ProductionAreas.Section_IV_V_FishFarming.type_fish.qty_sold_Aquaculture,
         fish_price = form.Section_IV_ProductionAreas.Section_IV_V_FishFarming.type_fish.fish_price_perunit,
         fish_installation_expense = form.Section_IV_ProductionAreas.Section_IV_V_FishFarming.type_fish.quanto_gastou_no_ltimo_ano_com_os_custos_de_instalaes_em_mzn_na_produo_de_p,
         fish_facilities_cost = form.Section_IV_ProductionAreas.Section_IV_V_FishFarming.type_fish.expenditures_facilities_Aquaculture,
         fish_equipment_expense = form.Section_IV_ProductionAreas.Section_IV_V_FishFarming.type_fish.expenditures_equipment_Aquaculture,
         fingerlings_expense = form.Section_IV_ProductionAreas.Section_IV_V_FishFarming.type_fish.expenditures_fingerlings_Aquaculture,
         fish_labour_cost = form.Section_IV_ProductionAreas.Section_IV_V_FishFarming.type_fish.expenditures_labor_Aquaculture,
         fish_maintenance_cost = form.Section_IV_ProductionAreas.Section_IV_V_FishFarming.type_fish.expenditures_other_Aquaculture,
         fish_days_of_work = form.Section_IV_ProductionAreas.Section_IV_V_FishFarming.type_fish.quantos_dias_por_semana_voc_trabalhou_para_piscicultura,
         fish_hours_of_work =form.Section_IV_ProductionAreas.Section_IV_V_FishFarming.type_fish.quantas_horas_por_dia_voc_trabalhou_para_piscicultura,
         fish_number_assisted_work = form.Section_IV_ProductionAreas.Section_IV_V_FishFarming.type_fish.se_sim_quantos_membros_da_famlia_ajudaram_voc_se_aplicvel_tambm_inclua_seu_,
         fish_assisted_days_work =form.Section_IV_ProductionAreas.Section_IV_V_FishFarming.type_fish.se_sim_em_mdia_quantos_dias_por_semana_eles_ajudaram_voc,
         fish_assisted_hours_work = form.Section_IV_ProductionAreas.Section_IV_V_FishFarming.type_fish.se_sim_em_mdia_quantas_horas_por_dia_eles_ajudaram_voc,
         fish_number_permanent_work = form.Section_IV_ProductionAreas.Section_IV_V_FishFarming.type_fish.quantos_trabalhadores_permanente_voc_contratou,
         fish_permanent_days_work = form.Section_IV_ProductionAreas.Section_IV_V_FishFarming.type_fish.em_mdia_por_quantos_dias_por_semana_voc_os_contratou,
         fish_permanent_hours_work = form.Section_IV_ProductionAreas.Section_IV_V_FishFarming.type_fish.em_mdia_quantas_horas_por_dia_eles_trabalharam_para_voc,
         fish_number_seasonal_work = form.Section_IV_ProductionAreas.Section_IV_V_FishFarming.type_fish.quantos_trabalhadores_sazonais_voc_contratou,
         fish_seasonal_days_work = `form.Section_IV_ProductionAreas.Section_IV_V_FishFarming.type_fish.copy-1-of-em_mdia_por_quantos_dias_por_semana_voc_os_contratou`,
         fish_seasonal_hours_work = `form.Section_IV_ProductionAreas.Section_IV_V_FishFarming.type_fish.copy-1-of-em_mdia_quantas_horas_por_dia_eles_trabalharam_para_voc`) %>%
  
  mutate(across(c(fish_qty_produced,fish_qty_sold,fish_price, fish_installation_expense,fish_facilities_cost,fish_equipment_expense,fingerlings_expense,fish_days_of_work,
                  fish_hours_of_work, fish_number_assisted_work, fish_assisted_days_work,fish_assisted_hours_work,fish_labour_cost,fish_maintenance_cost,fish_number_permanent_work,
                  fish_permanent_days_work,fish_permanent_hours_work,fish_number_seasonal_work,fish_seasonal_days_work,fish_seasonal_hours_work),as.numeric),
         # Calculating productivity and gross income for fisheries      
         fish_income = fish_price * fish_qty_sold,
         fish_total_expenses = rowSums(across(c(fish_installation_expense,fish_facilities_cost,fish_equipment_expense, fingerlings_expense,fish_labour_cost,
                                                fish_maintenance_cost))),
         fish_gross_income = fish_income * fish_total_expenses,
         fish_personallabour_time = fish_days_of_work * fish_hours_of_work,
         fish_assistedlabour_time = fish_number_assisted_work * fish_assisted_days_work * fish_assisted_hours_work,
         fish_permanentlabour_time = fish_number_permanent_work * fish_permanent_days_work * fish_permanent_hours_work,
         fish_seasonallabour_time = fish_number_seasonal_work * fish_seasonal_days_work * fish_seasonal_hours_work,
         fish_totallabr_days = rowSums(across(c(fish_personallabour_time,fish_assistedlabour_time,fish_permanentlabour_time,fish_seasonallabour_time))),
         fish_productivity = ifelse(fish_totallabr_days == 0, 0, (fish_qty_produced * fish_price) / fish_totallabr_days)) 

Gross_income_fish <- sum(Baseline_drought_fish$fish_gross_income)
# print(paste("Gross fish income for the population is", Gross_income_fish))

## Grouping data for merging
Baseline_dry_fish_grouped <- Baseline_drought_fish %>% 
  select(fish_qty_produced, fish_qty_sold, fish_price, formid, fish_income, fish_total_expenses, fish_gross_income, fish_personallabour_time, fish_assistedlabour_time, fish_permanentlabour_time,
         fish_seasonallabour_time, fish_totallabr_days, fish_productivity) %>% 
  group_by(formid) %>%
  summarise(across(where(is.numeric),  \(x) sum(x, na.rm = TRUE)), .groups = "drop")
```


```{r echo=FALSE, message=FALSE, warning=FALSE}
## Household decision indicators
## Importing data

Mangwana_Baseline_decisions <- read_excel("Mangwana - Baseline Survey.xlsx", 
                                          sheet = "Repeat- papel_...produo_e_renda")

## Selecting a subset of data 
Baseline_decisions <- Mangwana_Baseline_decisions %>% 
  
  
  
  mutate(across(everything(), ~ case_when(. == "---" ~ "0",
                                          . == " " ~ "0",
                                          is.na(.) ~ "0",
                                          TRUE ~ as.character(.)))) %>% 
  
  rename(extent_of_participation = form.seco_vi_papel_na_tomada_de_decises_no_lar_em_relao__produo_e_renda.seco_vi_papel_na_tomada_de_decises_no_lar_em_relao__produo_e_renda.papel_na_tomada_de_decises_no_lar_em_relao__produo_e_renda.em_que_medida_participou_na_tomada_de_decises_sobre_participou_nas_seguinte,
         extent_able_to_participate = form.seco_vi_papel_na_tomada_de_decises_no_lar_em_relao__produo_e_renda.seco_vi_papel_na_tomada_de_decises_no_lar_em_relao__produo_e_renda.papel_na_tomada_de_decises_no_lar_em_relao__produo_e_renda.em_que_medida_sente_que_pode_participar_das_decises_sobre_participou_nas_se,
         decision_product_quantity = form.seco_vi_papel_na_tomada_de_decises_no_lar_em_relao__produo_e_renda.seco_vi_papel_na_tomada_de_decises_no_lar_em_relao__produo_e_renda.papel_na_tomada_de_decises_no_lar_em_relao__produo_e_renda.qual_foi_a_sua_participao_nas_decises_sobre_a_quantidade_de_produtos_de_par,
         decision_income_utilization = form.seco_vi_papel_na_tomada_de_decises_no_lar_em_relao__produo_e_renda.seco_vi_papel_na_tomada_de_decises_no_lar_em_relao__produo_e_renda.papel_na_tomada_de_decises_no_lar_em_relao__produo_e_renda.em_que_medida_participou_nas_decises_sobre_a_forma_de_utilizar_o_rendimento) %>%
  
  select(-c(number,number__1,form.seco_vi_papel_na_tomada_de_decises_no_lar_em_relao__produo_e_renda.seco_vi_papel_na_tomada_de_decises_no_lar_em_relao__produo_e_renda.papel_na_tomada_de_decises_no_lar_em_relao__produo_e_renda.Current_participou)) %>% 
  
  mutate(across(c(extent_of_participation,extent_able_to_participate,decision_product_quantity,decision_income_utilization),~case_when(.%in% c("participao_na_maioria_ou_em_todas_as_decises", "PARTICIPAÇÃO_EM_ALGUMAS_DECISÕES")~ 2,.%in% c("participao_na_maioria_ou_em_todas_as_decises", "participao_em_algumas_decises")~ 3, .%in% c("pouca_ou_nenhuma_participao_nas_decises", "no_aplicvel__nenhuma_deciso_tomada") ~ 0, TRUE ~ as.numeric(.))),## Creating binaries for the choices.
         #summed_decisions = rowSums(across(c(extent_of_participation,extent_able_to_participate,decision_product_quantity,decision_income_utilization))),
         ## Calculating binaries for various input in livelihood and income decision making. 
         extent_participation_binary = ifelse(extent_of_participation >= 2, 1,0),
         able_to_participate_binary = ifelse(extent_able_to_participate >= 3, 1,0),
         product_quantity_binary = ifelse(decision_product_quantity >=2, 1,0),
         income_utilization_binary = ifelse(decision_income_utilization >= 2, 1,0),
         input_decision_adequacy = extent_participation_binary + able_to_participate_binary,
         income_decision_adequacy = product_quantity_binary + income_utilization_binary) %>%
  group_by(formid) %>%
  summarise(across(where(is.numeric),  \(x) sum(x, na.rm = TRUE)), .groups = "drop") %>% 
  ## Calculating final input livelihood decisions adequacy. 
  mutate(input_adequacy_binary = ifelse(input_decision_adequacy >0, 1,0),
         
         ## Calculating final control over income use adequacy
         income_adequacy_binary = ifelse(income_decision_adequacy >0, 1,0))

# Calculating number of people with input adequacy
input_adequacy = sum(Baseline_decisions$input_adequacy_binary)
# print(paste("Number of people who make adequate decisions on input within the population is", input_adequacy))

# Calculating number of people with income adequacy
income_adequacy = sum(Baseline_decisions$income_adequacy_binary)
# print(paste("Number of people who make adequate decisions on income within the population is", income_adequacy))
  
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
## Using the Mangwana baseline data imported above to calculate resilience to shock among others (Section 6)
Baseline_data <- Baseline_drought_data %>%
  filter(form.Section_IV_ProductionAreas.que_tipo_de_inqurito_est_a_realizar == "inqurito_de_base_para_as_duas_ltimas_pocas") %>% 
  mutate(weather_warning = `form.Section_VII_ResilienceShocks_group.warnings_weather_or_nature-related_issues`,
         harvest_storage = form.Section_VII_ResilienceShocks_group.A_place_to_store_your_harvest,
         other_income_source = form.Section_VII_ResilienceShocks_group.what_else_do_you_do_to_support_your_family,
         financial_insurance = form.Section_VII_ResilienceShocks_group.in_case_of_production_losses,
         ability_dealing_shocks = form.Section_VII_ResilienceShocks_group.assess_ability_to_cope_with_shocks_livelihood,
         crop_rotation_conservation = form.Section_VIII_Conservation_Practises_group.quais_prticas_de_conservao_oa_senhora_implementa_na_sua_machamba,
         crop_rotation_binary = ifelse(grepl("rotao_de_culturas",crop_rotation_conservation),1,0),
         across(c(weather_warning,harvest_storage,other_income_source,financial_insurance,ability_dealing_shocks), ~ ifelse(. == "sim", 1,0)),
         total_resilience = rowSums(across(c(weather_warning,harvest_storage,other_income_source,financial_insurance,ability_dealing_shocks,crop_rotation_binary))),
         resilience = ifelse(total_resilience >= 3,1,0))

## Counting respondents who meet resilience to shock criteria

Resilience_to_shock <- sum(Baseline_data$resilience)
# print(paste("Number of people with adequate level of resilience to shock in the population is", Resilience_to_shock))   
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
### Merging data for sub group analyses
Mangwana_baseline_merged <- Baseline_drought_data %>% 
  left_join(Selected_Child_indicators %>%  select(formid,dds,all_5,ncd_protect,ncd_risk,gdr_score), by = c("formid" = "formid")) %>% 
  left_join(Selected_adult_indicators %>%  select(formid,adult_dds,adult_dss_binary,grains,pulses, nuts, diary, meat_fish, dark_leafy_veg,egg, vitamin_A_veg, vitamin_A_fruit, other_fruit, adult_all_5,adult_all_5_binary,adult_ncd_protect,adult_ncd_protect_binary, adult_ncd_risk,adult_ncd_risk_binary, adult_gdr_score, carbs, fruit, vegetable, proteins, pulse), by = c("formid" = "formid")) %>% 
  left_join(Resilience %>%  select(formid,MAHFP,hhs_score,hunger_scores), by = c("formid" = "formid")) %>% 
  left_join(Baseline_drought_grouped %>%  select(qty_sold_kg,price_per_unit_sold,qty_prod_kg, cropland_ha, formid, personallabour_time,assistedlabour_time,personallabour_days,assistedlabour_days,paidlabour_days,total_labour_days, crops_income,productivity,total_expense,crop_yield,gross_agric_income), by = c("formid" = "formid")) %>% 
  left_join(Baseline_rainy_grouped %>%  select(rainy_qty_sold_kg, rainy_price_per_unit_sold,rainy_qty_prod_kg, rainy_cropland_ha, formid, rainy_total_weeks_fieldwork,rainy_personallabour_time, rainy_assistedlabour_time, rainy_paidlabour_time, rainy_personallabour_days,rainy_assistedlabour_days,rainy_paidlabour_days,rainy_total_labour_days, rainy_crops_income, rainy_productivity, rainy_total_expense,rainy_crop_yield, rainy_gross_agric_income), by = c("formid" = "formid")) %>% 
  left_join(Baseline_dry_forestry_grouped %>%  select(agro_crop_ha, agro_sale_price, agro_qty_sold_kg, agro_qty_prod_kg, formid, forest_crop_income, forest_total_expenses, forest_gross_income, forest_personallabour_time, forest_assistedlabour_time,forest_permantlabr_time, forest_seasonallabr_time, forest_totallabr_days, forest_productivity), by = c("formid" = "formid")) %>%
  left_join(Baseline_dry_animals_grouped %>%  select(formid, livestock_income, livestock_total_expense, gross_livestock_income, livestock_personallabour_time, livestock_assistedlabour_time,livestock_permanentlabour_time, livestock_seasonallabour_time, total_livestock_labour_time, livestock_productivity), by = c("formid" = "formid")) %>%
  left_join(Baseline_dry_fish_grouped %>%  select(fish_qty_produced, fish_qty_sold, fish_price, formid, fish_income, fish_total_expenses, fish_gross_income, fish_personallabour_time, fish_assistedlabour_time, fish_permanentlabour_time,fish_seasonallabour_time, fish_totallabr_days, fish_productivity), by = c("formid" = "formid")) %>% 
  left_join(Baseline_decisions %>%  select(formid, input_decision_adequacy, income_decision_adequacy, input_adequacy_binary,income_adequacy_binary), by = c("formid" = "formid")) %>%
  left_join(Baseline_data %>%  select(formid, total_resilience, resilience), by = c("formid" = "formid")) %>% 
  mutate(total_gross_income = rowSums(across(c(gross_agric_income,rainy_gross_agric_income,forest_gross_income,gross_livestock_income,fish_gross_income), ~ replace_na(as.numeric(.), 0))))
```

```{r message=FALSE, warning=FALSE, include=FALSE}
### Saving output into Excel file
output_file <- "Mangwana_baseline_results.xlsx"

if (file.exists(output_file)) {
  file.remove(output_file)
}

write_xlsx(Mangwana_baseline_merged, output_file)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
### Nutrition analyses for adult subgroups

#### Gender and age categorisation
Mangwana_baseline_result <- read_excel("Mangwana_baseline_results.xlsx") %>% 
  mutate(form.Section_I_group.Idade = as.numeric(form.Section_I_group.Idade),
         age_group = case_when(is.na (form.Section_I_group.Idade) ~ "",
                               form.Section_I_group.Idade < 18 ~ "< 18",
                               form.Section_I_group.Idade <=35 ~ "18 - 35",
                               form.Section_I_group.Idade > 35 ~ "> 35"),
         age_mdd_calc = case_when(is.na (form.Section_I_group.Idade) ~ "",
                                  form.Section_I_group.Idade < 15 ~ "< 15",
                                  form.Section_I_group.Idade <=49 ~ "15 - 49",
                                  form.Section_I_group.Idade > 49 ~ "> 49"),
         total_productivity = rowSums(across(c(productivity, rainy_productivity, forest_productivity,
                                               livestock_productivity, fish_productivity), ~ replace_na(.x, 0))),
         PPP_gross_household = total_gross_income/ PPP,
         PPP_per_day = PPP_gross_household / 365,# Calculating PPP per day to compare with  global threshold of 2.15$/day
         total_agric_income = rowSums(across(c(crops_income, rainy_crops_income), ~ replace_na(.x, 0)))) %>% 
  rename(gender = form.Section_I_group.Sexo) %>% 
  mutate(gender = case_when(
    gender == "feminino" ~ "female",
    gender == "masculino" ~ "male",
    TRUE ~ gender))
```

```{r message=FALSE, warning=FALSE, include=FALSE}
### Saving final output into Excel file
final_output_file <- "Mangwana_baseline_finalresult.xlsx"

if (file.exists(final_output_file)) {
  file.remove(final_output_file)
}

write_xlsx(Mangwana_baseline_result, final_output_file)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
#### Calculating MDD-W percentage
mdd_w <- Mangwana_baseline_result %>% 
  filter(gender == "female", age_mdd_calc == "15 - 49")
mean_mdd_w <- round(mean(mdd_w$adult_dds),1) # Calculating the average MDD-W score for the females between ages 15 and 49 years 
# print(paste("Average MDD_W for the females between 15 and 49 is", mean_mdd_w))
median_mdd_w <-median(mdd_w$adult_dds) # Calculating the median MDD-W score for the females between ages 15 and 49 years
# print(paste("Medium MDD_W for the females between 15 and 49 is", median_mdd_w)) # the median is used to check for outlier; whether the median is far from the mean.

mdd_w_percentage <- mdd_w %>% 
  group_by(adult_dds) %>% 
  summarise(mdd_w_category = n()) %>%
  mutate (percentage = round(mdd_w_category / sum(mdd_w_category)*100))
# print(mdd_w_percentage)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
#### Percentage of adult GDR score per gender and age group
gender_adult_gdr_percentage <- Mangwana_baseline_result %>%
  filter(gender != "---") %>% 
  group_by(adult_gdr_score,gender) %>% 
  summarise(Count = n(), .groups = "drop") %>% 
  mutate(Percentage = round((Count / sum(Count)) * 100, 1))

age_adult_gdr_percentage <- Mangwana_baseline_result %>%
  filter(gender != "---") %>% 
  group_by(adult_gdr_score, age_group) %>% 
  summarise(Count = n(), .groups = "drop") %>% 
  mutate(Percentage = round((Count / sum(Count)) * 100, 1))

```

```{r echo=FALSE, message=FALSE, warning=FALSE}
#### DSS per gender and age group
gender_dds_percentage <- Mangwana_baseline_result %>%
  filter(gender != "---" ) %>% # , adult_dss_binary == 1
  group_by(gender, adult_dss_binary) %>% 
  summarise(dds_count = n(), .groups = "drop") %>%
  mutate (percentage = round(dds_count / sum(dds_count)*100))
# print(gender_dds_percentage)

age_dds_percentage <- Mangwana_baseline_result %>%
  filter(gender != "---") %>% #, adult_dss_binary == 1
  group_by(age_group, adult_dss_binary) %>% 
  summarise(dds_count = n(), .groups = "drop") %>%
  mutate (percentage = round(dds_count / sum(dds_count)*100))
# print(age_dds_percentage)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
#### All 5 per gender and age group
gender_all5_percentage <- Mangwana_baseline_result %>%
  filter(gender != "---",  adult_all_5_binary ==1) %>% 
  group_by(gender, adult_all_5_binary) %>% 
  summarise(count = n(), .groups = "drop") %>%
  mutate (percentage = round(count / sum(count)*100))
# print(gender_all5_percentage)

age_all5_percentage <- Mangwana_baseline_result %>%
  filter(gender != "---", adult_all_5_binary ==1) %>% 
  group_by(age_group, adult_all_5_binary) %>% 
  summarise(count = n(), .groups = "drop") %>%
  mutate (percentage = round(count / sum(count)*100))
# print(age_all5_percentage)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
#### NCD-protect per gender and age group
gender_ncdprotect_percentage <- Mangwana_baseline_result %>%
  filter(gender != "---",  adult_ncd_protect_binary ==1) %>% 
  group_by(gender, adult_ncd_protect_binary) %>% 
  summarise(ncdprotect_category = n(), .groups = "drop") %>%
  mutate (percentage = round(ncdprotect_category / sum(ncdprotect_category)*100))
# print(gender_ncdprotect_percentage)

age_ncdprotect_percentage <- Mangwana_baseline_result %>%
  filter(gender != "---", adult_ncd_protect_binary ==1) %>% 
  group_by(age_group, adult_ncd_protect_binary) %>% 
  summarise(ncdprotect_category = n(), .groups = "drop") %>%
  mutate (percentage = round(ncdprotect_category / sum(ncdprotect_category)*100))
# print(age_ncdprotect_percentage)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
#### NCD-risk per gender and age group
gender_ncdrisk_percentage <- Mangwana_baseline_result %>%
  filter(gender != "---",  adult_ncd_risk_binary ==1) %>% 
  group_by(gender, adult_ncd_risk_binary) %>% 
  summarise(ncdrisk_category = n(), .groups = "drop") %>%
  mutate (percentage = round(ncdrisk_category  / sum(ncdrisk_category )*100))
# print(gender_ncdrisk_percentage)

age_ncdrisk_percentage <- Mangwana_baseline_result %>%
  filter(gender != "---", adult_ncd_risk_binary ==1) %>% 
  group_by(age_group, adult_ncd_risk_binary) %>% 
  summarise(ncdrisk_category  = n(), .groups = "drop") %>%
  mutate (percentage = round(ncdrisk_category  / sum(ncdrisk_category )*100))
# print(age_ncdrisk_percentage)
```


The number of respondents answering children DQQ questions: `r sum(Selected_Child_indicators$have_child)`

The number of adults interviewed: `r nrow(Mangwana_Baseline_Survey)`

The number of women interviewed: `r sum(Mangwana_baseline_result$gender == "female") `

The number youth (18-35) interviewed: `r sum(Mangwana_baseline_result$age_group == "18 - 35")`


# Number of people with diverse and adequate diet

# Children

## Ever breastfed

The percentage of children ever-breastfed is: `r paste0(round(breastfeeding$percent_breastfed,1), "%") ` 

## Early initiation of breastfeeding

The percentage of children breastfed within first hour of birth is: `r paste(round(immbreastfeeding$percent_early_breastfed, 1), "%") ` 

## DDS score

The average DDS score out of 10 for the children population is: `r round(mean_dds_score, 1)`

The distribution of DDS scores out of 10 for the children population is:
```{r}
dds_all <- Selected_Child_indicators %>%
  filter(have_child == 1,breastfed == 0) %>%
  group_by(dds) %>% 
  summarise(count = n()) %>%
  mutate (percentage = round(count / sum(count)*100))
kable(dds_all, caption = "Percentage of children DDS score")

ggplot(dds_all, aes(x= as.factor(dds), y = percentage, fill = as.factor(dds))) + 
  geom_bar(stat = "identity") +
  geom_text(aes(label = round(percentage, 1)), 
            vjust = -0.3,                        
            size = 4) +
  labs(title = "Percentage distribution of children DDS Scores",
       x = "DDS scores",
       y = "Percentage (%)", 
       fill = "Scores") +
  theme_minimal() +
  scale_x_discrete(limits = as.character(seq(0, 10, 1)))   +
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 20)) +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "none"
  )
```
```{r}
dds_foodgroup <- Selected_Child_indicators %>%
  filter(have_child == 1, breastfed == 0) %>%
  select(dds, processed_porridge, unprocessed_porridge, root_crop_porridge,
         beans, nuts, animal_milk, cheese, yoghurt,
         meat, sausages, pork_rabbit, poultry, fish, shrimp_snails,
         green_leafy_vegetables, leafy_vegetables,
         eggs,
         orange_vegetables, tomato_cabbage_mushroom, yellow_fruits, citrus, apples,
         long_cycle_fruits) %>%
  mutate(
    grains = pmax(processed_porridge, unprocessed_porridge, root_crop_porridge),
    pulses = beans,
    nuts = nuts,
    dairy = pmax(animal_milk, cheese, yoghurt),
    meat_fish = pmax(meat, sausages, pork_rabbit, poultry, fish, shrimp_snails),
    dark_leafy_veg = pmax(green_leafy_vegetables, leafy_vegetables),
    egg = eggs,
    vitamin_A_veg = pmax(orange_vegetables, tomato_cabbage_mushroom),
    vitamin_A_fruit = pmax(yellow_fruits, citrus, apples),
    other_fruit = long_cycle_fruits
  ) %>%
  select(dds, grains, pulses, nuts, dairy, meat_fish, dark_leafy_veg, egg, vitamin_A_veg, vitamin_A_fruit, other_fruit) %>%
  pivot_longer(cols = -dds, names_to = "DSS_foodgroup", values_to = "Number") %>%
  filter(Number == 1) %>%
  group_by(dds, DSS_foodgroup) %>%
  summarise(count = n(), .groups = 'drop') %>%
  group_by(dds) %>%
  mutate(
    percentage = round(count / sum(count) * 100, 1),
    pos = cumsum(percentage) - 0.5 * percentage
  ) %>%
  ungroup()

ggplot(dds_foodgroup, aes(x = as.factor(dds), y = percentage, fill = DSS_foodgroup)) + 
  geom_bar(stat = "identity") +
  geom_text(aes(y = pos, label = percentage), color = "black", size = 3) +
  labs(title = "Distribution of DDS scores per Food Group",
       x = "DDS score",
       y = "Percentage (%)",
       fill = "Food group") +
  theme_minimal() +
  scale_x_discrete(limits = as.character(seq(0, 10, 1)))   +
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 10)) +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "right"
  )
```


## All-5 score

The percentage of the children's  population consuming all five recommended food groups the previous day or night:

```{r}
kable(all_5_percentage, caption = "Percentage of children all 5 score")
ggplot(all_5_percentage, aes(x= as.factor(all_5), y = percentage, fill = as.factor(all_5))) + 
  geom_bar(stat = "identity") +
  geom_text(aes(label = round(percentage, 1)), 
            vjust = -0.3,                        
            size = 4) +
  labs(title = "Percentage distribution of children All - 5 scores",
       x = "All 5 score",
       y = "Percentage (%)", 
       fill = "Scores") +
  theme_minimal() + 
  scale_x_discrete(limits = as.character(seq(0, 5, 1)))   +
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 20)) +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "none"
  )
```


```{r}
all5_foodgroup <- Selected_Child_indicators %>% 
  filter(have_child == 1, breastfed == 0) %>%
  mutate(starchy_staples = as.integer(rowSums(across(c(processed_porridge, unprocessed_porridge, root_crop_porridge)) == 1, na.rm = TRUE) > 0),
    vegetables = as.integer(rowSums(across(c(green_leafy_vegetables, leafy_vegetables, orange_vegetables, tomato_cabbage_mushroom, salad_vegetables)) == 1, na.rm = TRUE) > 0),
    fruits = as.integer(rowSums(across(c(yellow_fruits, citrus, long_cycle_fruits, apples)) == 1, na.rm = TRUE) > 0),
    pulses_nuts_seeds = as.integer(rowSums(across(c(beans, nuts)) == 1, na.rm = TRUE) > 0),
    animal_source_foods = as.integer(rowSums(across(c(animal_milk, yoghurt, eggs, cheese, sausages, meat, poultry, fish, shrimp_snails)) == 1, na.rm = TRUE) > 0)) %>% 
  select(all_5, starchy_staples, vegetables, fruits, pulses_nuts_seeds, animal_source_foods) %>%
  pivot_longer(cols = -all_5, names_to = "Food_group", values_to = "Number") %>%
  filter(Number == 1) %>%
  group_by(all_5, Food_group) %>%
  summarise(count = n(), .groups = 'drop') %>%
  group_by(all_5) %>%
  mutate(
    percentage = round(count / sum(count) * 100, 1),
    pos = cumsum(percentage) - 0.5 * percentage
  )
ggplot(all5_foodgroup, aes(x = as.factor(all_5), y = percentage, fill = Food_group)) +
  geom_bar(stat = "identity") +
  geom_text(aes(y = pos, label = percentage)) +
  labs(
    title = "Percentage of children consuming All_5 food group",
    x = "Food group",
    y = "Percentage (%)"
  ) +
  theme_minimal() +
  scale_x_discrete(limits = as.character(seq(0, 5, 1)))   +
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 10)) +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "right")
```


## NCD-Protect score

The average NCD-Protect score out of 9 for the children population is: `r round(mean_ncd_protect_score, 1)`

## NCD-Risk score

The average NCD-Risk score out of 9 for the children population is: `r round(mean_ncd_risk_score, 1)`

## GDR score

The average GDR score out of 18 for the children population is: `r round(mean_gdr_score, 1)`

The distribution of the GDR scores out of 18 is:
```{r}
kable(gdr_percentage, caption = "Percentage of children's GDR score")

### Graphing the GDR score
ggplot(gdr_percentage, aes(x= as.factor(gdr_score), y = Percentage, fill = as.factor(gdr_score))) + 
  geom_bar(stat = "identity") +
  geom_text(aes(label = round(Percentage, 1)), 
            vjust = -0.3,                        
            size = 4) +
  labs(title = "Percentage distribution of children GDR Scores",
       x = "Specific GDR score",
       y = "Percentage (%)", 
       fill = "Categories") +
  theme_minimal() + 
  scale_x_discrete(limits = as.character(seq(6, 18, 1)))   +
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 50)) +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "none"
  ) 
```

# Adults

## DDS and MDD-W score

The average DDS score out of 10 for adults is: `r round(avg_dds_score, 1)`

The average DDS score out of 10 for youth (18-35 years) is: `r round(mean(Mangwana_baseline_result$adult_dds [Mangwana_baseline_result$age_group == "18 - 35"], na.rm = TRUE),1)`

## DDS per population and subgroups

```{r}
kable(adult_dds_percentage, caption = "DDS percentage per population")
```

```{r}
kable(gender_dds_percentage, caption = "DDS percentage per gender")
```

```{r}
gender_youth_dds_percentage <- Mangwana_baseline_result %>%
  filter(gender != "---", age_group == "18 - 35") %>% #, adult_dss_binary == 1
  group_by(gender, adult_dss_binary) %>% 
  summarise(count = n(), .groups = "drop") %>%
  mutate (percentage = round(count / sum(count)*100))
kable(gender_youth_dds_percentage, caption = "DDS percentage per gender and youth")
```

```{r}
kable(age_dds_percentage, caption = "DDS percentage per age group")
```

The distribution of the DDS scores out of 10 among adults is:

```{r}
ggplot(adult_dds_percentage, aes(x= as.factor(adult_dds), y = percentage, fill = as.factor(adult_dds))) + 
  geom_bar(stat = "identity") +
  geom_text(aes(label = round(percentage, 1)), 
            vjust = -0.3,                        
            size = 4) +
  labs(title = "Percentage distribution of Adult DDS Scores",
       x = "DDS scores",
       y = "Percentage (%)", 
       fill = "Scores") +
  theme_minimal() +
  scale_x_discrete(limits = as.character(seq(0, 10, 1)))   +
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 20)) +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "none"
  )
```

```{r}
adult_youth_dds_percentage <- Mangwana_baseline_result %>%
  filter(age_group == "18 - 35") %>% 
  group_by(adult_dds) %>% 
  summarise(count = n()) %>%
  mutate (percentage = round(count / sum(count)*100))

ggplot(adult_youth_dds_percentage, aes(x= as.factor(adult_dds), y = percentage, fill = as.factor(adult_dds))) + 
  geom_bar(stat = "identity") +
  geom_text(aes(label = round(percentage, 1)), 
            vjust = -0.3,                        
            size = 4) +
  labs(title = "Percentage distribution of Adult youth DDS Scores",
       x = "DDS scores",
       y = "Percentage (%)", 
       fill = "Scores") +
  theme_minimal() +
  scale_x_discrete(limits = as.character(seq(0, 10, 1)))   +
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 20)) +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "none"
  )
```


The percentage of women of reproductive age (15-49 years) meeting the MDD-W  is: `r female_mddw_age <- sum(
    Mangwana_baseline_result$gender == "female" &
    Mangwana_baseline_result$age_mdd_calc == "15 - 49" &
    Mangwana_baseline_result$adult_dss_binary == 1,
    na.rm = TRUE
  )
  total_rows <- sum(Mangwana_baseline_result$gender == "female" &
  Mangwana_baseline_result$age_mdd_calc == "15 - 49")

  if (total_rows == 0) {
    "0 (no data)"
  } else {
    paste0(round(100 * (female_mddw_age / total_rows), 1), "%")
  }`
  
Average MDD-W for the women between 15 and 49 is: `r female_mddw_age <- sum(
    Mangwana_baseline_result$gender == "female" &
    Mangwana_baseline_result$age_mdd_calc == "15 - 49" &
    Mangwana_baseline_result$adult_dss_binary == 1,
    na.rm = TRUE
  )
  total_rows <- sum(Mangwana_baseline_result$gender == "female" &
  Mangwana_baseline_result$age_mdd_calc == "15 - 49")
  if (total_rows == 0) {
    "0 (no data)"
  } else {
    paste0(round(female_mddw_age / total_rows, 1))
  }`

The distribution of the MDD-W out of 10 among women of reproductive age (15-49 years) is:

```{r}
adult_mddw_percentage <- Mangwana_baseline_result %>%
  filter(gender == "female", age_mdd_calc == "15 - 49") %>% 
  group_by(adult_dds) %>% 
  summarise(count = n()) %>%
  mutate (percentage = round(count / sum(count)*100))
kable(adult_mddw_percentage, caption = "MDD-W among women of reproductive age (15-49 years) ")

ggplot(adult_mddw_percentage, aes(x= as.factor(adult_dds), y = percentage, fill = as.factor(adult_dds))) + 
  geom_bar(stat = "identity") +
  geom_text(aes(label = round(percentage, 1)), 
            vjust = -0.3,                        
            size = 4) +
  labs(title = "Percentage distribution of MDD-W Scores",
       x = "MDD-W scores",
       y = "Percentage (%)", 
       fill = "Scores") +
  theme_minimal() +
  scale_x_discrete(limits = as.character(seq(0, 10, 1)))   +
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 20)) +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "none"
  )
```

```{r}
adult_mddw_percentage <- Mangwana_baseline_result %>%
  filter(gender == "female", age_mdd_calc == "15 - 49") %>%
  select(adult_dds,grains,pulses, nuts, diary, meat_fish, dark_leafy_veg,egg, vitamin_A_veg, vitamin_A_fruit, other_fruit) %>% 
  pivot_longer(cols = c(grains,pulses, nuts, diary, meat_fish, dark_leafy_veg,egg, vitamin_A_veg, vitamin_A_fruit, other_fruit),
               names_to = "DSS_Foodgroup",
               values_to = "Number") %>%
  filter(Number == 1) 
food_group_order <- c("grains", "pulses", "nuts", "diary", "meat_fish", 
                      "dark_leafy_veg", "egg", "vitamin_A_veg", 
                      "vitamin_A_fruit", "other_fruit")
  adult_mddw_percentage$DSS_Foodgroup <- factor(
  adult_mddw_percentage$DSS_Foodgroup,
  levels = food_group_order
)
adult_mddw_percentage <- adult_mddw_percentage %>%
  group_by(adult_dds, DSS_Foodgroup) %>% 
  summarise(count = n(), .groups = 'drop') %>% 
    group_by(adult_dds) %>% 
    arrange(factor(DSS_Foodgroup, levels = food_group_order)) %>%
    mutate(percentage = round(count / sum(count) * 100, 1),
         pos = cumsum(percentage) - (0.5 * percentage)) %>%
  ungroup()
kable(adult_mddw_percentage %>% 
        select(adult_dds, DSS_Foodgroup, count, percentage), 
      caption = "MDD-W among women of reproductive age (15-49 years)")

ggplot(adult_mddw_percentage, aes(x= as.factor(adult_dds), y = percentage, fill = DSS_Foodgroup)) + 
  geom_bar(stat = "identity") +
  # geom_text(aes(y = pos, label = percentage), color = "white", size = 3) +
  scale_fill_manual(values = c(
    "grains" = "#E69F00",
    "pulses" = "#56B4E9",
    "nuts" = "#009E73",
    "diary" = "#F0E442",
    "meat_fish" = "#0072B2",
    "dark_leafy_veg" = "#D55E00",
    "egg" = "#CC79A7",
    "vitamin_A_veg" = "#999999",
    "vitamin_A_fruit" = "#A65628",
    "other_fruit" = "#FF69B4"
  )) +
  labs(title = "Distribution of MDD-W Scores per food group (%)",
       x = "MDD-W scores",
       y = "Percentage (%)", 
       fill = "Food group") +
  theme_minimal() +
  scale_x_discrete(limits = as.character(seq(0, 8, 1)))   +
  scale_y_continuous(limits = c(0, 105), breaks = seq(0, 100, 10)) +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "right"
  )
```


## All-5 score

The percentage of the adult population consuming all five recommended food groups the previous day or night: `r paste0(round(100 * sum(Mangwana_baseline_result$adult_all_5_binary == 1) / nrow(Mangwana_baseline_result), 1), "%")`

The average of the adult population consuming all five recommended food groups the previous day or night:`r round(avg_all_5_score, 1)`

The percentage of youth (18-35) consuming all five recommended food groups the previous day or night: `r paste0(round(100 * sum(Mangwana_baseline_result$age_group == "18 - 35" & Mangwana_baseline_result$adult_all_5_binary == 1 ) / sum(Mangwana_baseline_result$adult_all_5_binary), 1), "%")`

```{r echo=FALSE, message=FALSE, warning=FALSE}
#### Presenting percentages and graph of adult All-5 
## Calculating the percentage of adult All 5 scores
adult_all_5_percentage <- Selected_adult_indicators %>%
  group_by(adult_all_5) %>% 
  summarise(count = n()) %>%
  mutate (percentage = round(count / sum(count)*100))

kable(adult_all_5_percentage, caption = "Percentage of adult All 5 scores")

# Graph adult's all 5 categories

ggplot(adult_all_5_percentage, aes(x= as.factor(adult_all_5), y = percentage, fill = as.factor(adult_all_5))) + 
  geom_bar(stat = "identity") +
  geom_text(aes(label = round(percentage, 1)), 
            vjust = -0.3,                        
            size = 4) +
  labs(title = "Percentage distribution of All-5 Scores for adult population",
       x = "All 5 categories",
       y = "Percentage (%)", 
       fill = "Categories") +
  theme_minimal() +
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 20)) +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "none"
  )
```

### All-5 percentage per gender and age-group
```{r}
kable(gender_all5_percentage, caption = "All-5 percentage per gender")
```

```{r}
kable(age_all5_percentage, caption = "All-5 percentage per age-group")
```

```{r}
all5_percentage_gd_age <- Mangwana_baseline_result %>%
  filter( adult_all_5_binary ==1) %>% 
  group_by(gender, age_group, adult_all_5_binary) %>% 
  summarise(count = n(), .groups = "drop") %>%
  mutate (percentage = round(count / sum(count)*100))

ggplot(all5_percentage_gd_age, aes(x = age_group, y = percentage, fill = age_group)) +
  geom_bar(stat = "identity") +
  facet_wrap(~gender) +
  labs(
    title = "Percentage of adults subs consuming All 5 food groups",
    x = "Age Group",
    y = "Percentage (%)"
  ) +
  theme_minimal() +
  geom_text(aes(label = paste0(percentage)), vjust = -0.3, size = 3) +
  guides(fill = "none") +
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 20)) +

  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  )

```

```{r echo=FALSE, message=FALSE, warning=FALSE}
#### Presenting percentages and graph of adult consuming specific foods.
## The percentage of adult consuming a specific food group
adult_specific_all_5_group <-Selected_adult_indicators %>% 
  select(carbs,fruit,vegetable, proteins, pulse) %>% 
  summarise(round(across(everything(),~ mean(.==1) *100))) %>% 
  pivot_longer(cols = everything(), names_to = "Food Group", values_to = "Percentage")
kable(adult_specific_all_5_group, caption = "Percentage of adult consuming a specific food group")

## ## Graph for percentage of adult consuming a specific food group
ggplot(adult_specific_all_5_group, aes(x= reorder(as.factor(`Food Group`), -Percentage), y = Percentage, fill = as.factor(`Food Group`))) + 
  geom_bar(stat = "identity") +
  geom_text(aes(label = round(Percentage, 1)), 
            vjust = -0.3,                        
            size = 4) +
  labs(title = "Percentage of adult population",
       x = "Specific categories for All 5 group",
       y = "Percentage (%)", 
       fill = "Categories") +
  theme_minimal() + 
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 20)) +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "none"
  )
```


```{r}
adult_gender_specific_all_5_group <-Mangwana_baseline_result %>%
  group_by(gender, age_group) %>%
  select(carbs,fruit,vegetable, proteins, pulse) %>% 
  summarise(round(across(everything(),~ mean(.==1) *100)), .groups = "drop") %>% 
  pivot_longer(cols = c(carbs, fruit, vegetable, proteins, pulse), names_to = "Food Group", values_to = "Percentage")
kable(adult_gender_specific_all_5_group, caption = "Percentage of specific group by gender and age")

ggplot(adult_gender_specific_all_5_group, aes(x= reorder(as.factor(`Food Group`), -Percentage), y = Percentage, fill = gender)) + 
  geom_bar(stat = "identity", position = position_dodge(width = 0.8)) +
  geom_text(aes(label = round(Percentage, 1)), 
            position = position_dodge(width = 0.8),
            vjust = -0.3,                        
            size = 3) +
  facet_wrap(~ age_group) +
  labs(title = "Percentage of adult population",
       x = "Specific categories for All 5 group",
       y = "Percentage (%)", 
       fill = "Categories") +
  theme_minimal() + 
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 10)) +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(), axis.text.x = element_text(angle = 45, hjust = 1)
  )
```

## NCD-Protect score

The average NCD-Protect score out of 9 for the adult population is: `r round(avg_ncd_protect_score,1)`

The average NCD-Protect score out of 9 for women is:`r round(mean(Mangwana_baseline_result$adult_ncd_protect[Mangwana_baseline_result$gender == "female"], na.rm = TRUE),1)` 

The percentage of women with NCD protect score of 1 is: `r paste0(round(100 * sum(Mangwana_baseline_result$gender == "female" & Mangwana_baseline_result$adult_ncd_protect_binary == 1 ) / sum(Mangwana_baseline_result$adult_ncd_protect_binary), 1), "%")`

The average NCD-Protect score out of 9 for youth (18-35) is: `r round(mean(Mangwana_baseline_result$adult_ncd_protect[Mangwana_baseline_result$age_group == "18 - 35"], na.rm = TRUE),1)` 

The percentage of youth (18-35) with NCD protect score of 1 is: `r paste0(round(100 * sum(Mangwana_baseline_result$age_group == "18 - 35" & Mangwana_baseline_result$adult_ncd_protect_binary == 1 ) / sum(Mangwana_baseline_result$adult_ncd_protect_binary), 1), "%")`


## NCD-Risk score

The average NCD-Risk score out of 9 for the adult population is: `r round(avg_ncd_risk_score,1)`

The average NCD-Risk score out of 9 for women is:`r round(mean(Mangwana_baseline_result$adult_ncd_risk[Mangwana_baseline_result$gender == "female"], na.rm = TRUE),1)` 

The percentage of women with NCD-Risk score of 1 is: `r paste0(round(100 * sum(Mangwana_baseline_result$gender == "female" & Mangwana_baseline_result$adult_ncd_risk_binary == 1 ) / sum(Mangwana_baseline_result$adult_ncd_risk_binary), 1), "%")`

The average NCD-Risk score out of 9 for youth (18-35) is: `r round(mean(Mangwana_baseline_result$adult_ncd_risk[Mangwana_baseline_result$age_group == "18 - 35"], na.rm = TRUE),1)` 
The percentage of youth (18-35) with NCD-Risk score of 1 is: `r paste0(round(100 * sum(Mangwana_baseline_result$age_group == "18 - 35" & Mangwana_baseline_result$adult_ncd_risk_binary == 1 ) / sum(Mangwana_baseline_result$adult_ncd_risk_binary), 1), "%")`


## GDR score

The average GDR score out of 18 for the adult population is: `r round(avg_gdr_score,1)`

The average GDR score out of 9 for women is:`r round(mean(Mangwana_baseline_result$adult_gdr_score[Mangwana_baseline_result$gender == "female"], na.rm = TRUE),1)` 

The average GDR score out of 9 for youth (18-35) is: `r round(mean(Mangwana_baseline_result$adult_gdr_score[Mangwana_baseline_result$age_group == "18 - 35"], na.rm = TRUE),1)` 

The distribution of the GDR score out of 18 for adults is:
```{r echo=FALSE, message=FALSE, warning=FALSE}
#### Presenting percentages and graph of adult GDR score.  
### Graphing the GDR score
  ## Percentage of adult GDR score 
## Note: I did not round the figures to prevent 0 for some categories. If needed, I can round the figures to a whole number
  
## Percentage of adult GDR score

adult_gdr_percentage <- Selected_adult_indicators %>% 
  group_by(adult_gdr_score) %>% 
  summarise(Count = n()) %>% 
  mutate(Percentage = round((Count / sum(Count)) * 100))

### Graphing the GDR score
ggplot(adult_gdr_percentage, aes(x= as.factor(adult_gdr_score), y = Percentage, fill = as.factor(adult_gdr_score))) + 
  geom_bar(stat = "identity") +
  geom_text(aes(label = round(Percentage, 1)), 
            vjust = -0.3,                        
            size = 4) +
  labs(title = "Percentage distribution of GDR Scores",
       x = "Specific GDR score",
       y = "Percentage (%)", 
       fill = "Categories") +
  theme_minimal() + 
    scale_x_discrete(limits = as.character(seq(0, 18, 1)))   +
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 20)) +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "none"
  )   
```

Distribution of adult GDR score per gender: 
```{r}
kable(gender_adult_gdr_percentage, caption = "Percentage of GDR score per gender")

## Graph for GDR score per gender


ggplot(gender_adult_gdr_percentage, aes(x = factor(adult_gdr_score), y = Percentage, fill = gender)) +
  geom_bar(stat = "identity", 
           #position = position_dodge(width = 0.8), 
           width = 0.7) +  
  geom_text(aes(label = round(Percentage, 1)),
            vjust = -0.3,
            size = 2,
            position = position_stack(vjust = 0.5)) +
  labs(
    title = "Percentage of GDR score by gender",
    x = "GDR Score",
    y = "Percentage (%)",
    fill = "Categories"
  ) +
  theme_minimal() +
  scale_x_discrete(limits = as.character(seq(6, 18, 1))) +
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 50, 5)) +
  guides(fill = guide_legend(title = "Categories")) +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text.x = element_text(size = 10),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 9)
  )


```

Distribution of adult GDR score per youth:
```{r}
kable(age_adult_gdr_percentage, caption = "Percentage of GDR score per age group")

## Graph for GDR score per gender

ggplot(age_adult_gdr_percentage, aes(x = factor(adult_gdr_score), y = Percentage, fill = age_group)) +
  geom_bar(stat = "identity" , width = 0.8) + # position = position_dodge(width = 1),
  labs(
    title = "Percentage of GDR score by age group",
    x = "GDR Score",
    y = "Percentage (%)",
    fill = "Categories"
  ) +
  theme_minimal() +
  geom_text(aes(label = paste0(Percentage)), vjust = -0.3, size = 2, position = position_stack(vjust = 0.5)) +
  guides(fill = guide_legend(title = "Categories")) +
  scale_x_discrete(limits = as.character(seq(6, 18, 1))) +
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 50, 5)) +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  )



```


# Number of people whose nutritional situation became more resilient to shocks

## MAHFP score

The average MAHFP score for the total population is:  `r Average_MAHFP`

The target average MAHFP score for follow up is: `r mean_top_third`

```{r echo=FALSE}
ggplot(MAHFP_months, aes(x = months, y = n, fill = months)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n), vjust = -0.3, size = 3.5) +
  labs(
    title = "Frequency of months with missed foods",
    x = "Month",
    y = "Number"
  ) +
  theme_minimal() +
  scale_y_continuous(limits = c(0, 140), breaks = seq(0, 140, 20)) +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text.x = element_blank(),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 9)
  )
```


## HHS score

The median HHS score for the total population is: `r Median_hhs_score`

The distribution of the HHS score for the total population is:  
```{r}
kable(HHS_percentage, caption = "Percentage of HHS scores")

ggplot(HHS_percentage, aes(x = hunger_scores, y = Percentage, fill = hunger_scores)) +
  geom_bar(stat = "identity", width = 0.8) +
  labs(
    title = "Percentage of HHS score",
    x = "HHS Score",
    y = "Percentage (%)",
    fill = "Categories"
  ) +
  theme_minimal() +
  geom_text(aes(label = paste0(Percentage)), vjust = -0.3, size = 5) +
  guides(fill = guide_legend(title = "Categories")) +

  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 20)) +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text.x = element_text(angle = 25, vjust = 1, hjust = 0.5)
  )

```


# Number of SSFPs who doubled productivity

The average productivity (income/ # of working days) per household is: `r format(round(mean(Mangwana_baseline_result$total_productivity, na.rm = TRUE), 1), scientific = FALSE)`


# Number of SSFP who progressively decrease the yield gap 

The average yield (kg/hectare) per household for the dry season is: `r round(mean(Mangwana_baseline_result$crop_yield, na.rm = TRUE),1)`

The average yield (kg/hectare) per household for the rainy season is:`r round(mean(Mangwana_baseline_result$rainy_crop_yield, na.rm = TRUE),1)`

# Income

## PPP per day for each household

Average PPP gross income for per day the population is: `r round(mean(Mangwana_baseline_result$PPP_per_day),1)`

## Agriculture

### Baseline dry season crops

The average income per household for dry season crops is: `r format(round(mean(Mangwana_baseline_result$crops_income, na.rm = TRUE), 1), scientific = FALSE)`

The standard deviation of income per household for dry season crops is: `r format(round(sd(Mangwana_baseline_result$crops_income, na.rm = TRUE), 1), scientific = FALSE)`

The average gross income per household for dry season crops is: `r format(round(mean(Mangwana_baseline_result$gross_agric_income, na.rm = TRUE), 1), scientific = FALSE)`

The standard deviation of the gross income per household for dry season crops is: `r format(round(sd(Mangwana_baseline_result$gross_agric_income, na.rm = TRUE), 1), scientific = FALSE)`

### Baseline rainy season crops

The average income per household for rainy season crops is: `r format(round(mean(Mangwana_baseline_result$rainy_crops_income, na.rm = TRUE), 1), scientific = FALSE)`

The standard deviation of income per household for rainy season crops is: `r format(round(sd(Mangwana_baseline_result$rainy_crops_income, na.rm = TRUE), 1), scientific = FALSE)`

The average gross income per household for rainy season crops is: `r format(round(mean(Mangwana_baseline_result$rainy_gross_agric_income, na.rm = TRUE), 1), scientific = FALSE)`

The standard deviation of the gross income per household for rainy season crops is: `r format(round(sd(Mangwana_baseline_result$rainy_gross_agric_income, na.rm = TRUE), 1), scientific = FALSE)`

The average agriculture income for both dry and rainy season is: `r format(round(mean(Mangwana_baseline_result$total_agric_income, na.rm = TRUE), 1), scientific = FALSE)`

The standard deviation of agriculture income for both dry and rainy season is: `r format(round(sd(Mangwana_baseline_result$total_agric_income, na.rm = TRUE), 1), scientific = FALSE)`

## Agroforestry

The average gross income for agroforestry is: `r round(mean(Mangwana_baseline_result$forest_gross_income, na.rm = TRUE),1)`

The standard deviation of gross income for agroforestry is: `r round(sd(Mangwana_baseline_result$forest_gross_income, na.rm = TRUE),1)`

## Livestock

The average gross income for livestock is: `r round(mean(Mangwana_baseline_result$gross_livestock_income, na.rm = TRUE),1)`

The standard deviation of gross income for livestock is: `r round(sd(Mangwana_baseline_result$gross_livestock_income, na.rm = TRUE),1)`

## Fish farming

The average gross income for fish farming is: `r round(mean(Mangwana_baseline_result$fish_gross_income, na.rm = TRUE),1)`

The standard deviation of gross income for fish farming is: `r round(sd(Mangwana_baseline_result$fish_gross_income, na.rm = TRUE),1)`


# Number of female SSFP who progressively become more empowered

The number of women who make adequate decisions on input within the population is: `r sum(Mangwana_baseline_result$gender == "female" & Mangwana_baseline_result$input_adequacy_binary == 1 )`

The number of women who make adequate decisions on income within the population is: `r sum(Mangwana_baseline_result$gender == "female" & Mangwana_baseline_result$income_adequacy_binary == 1)`

# Number of SSFP whose livelihoods became more resilient to shocks

The number of people with adequate level of resilience to shock in the population is: `r sum(Mangwana_baseline_result$resilience)`
